---
title: "Example: Mean off-time reduction in Parkinson's disease"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{Example: Mean off-time reduction in Parkinson's disease}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8, 
  fig.height = 6,
  eval = identical(Sys.getenv("NOT_CRAN"), "true")
)
options(width = 100)
```

```{r setup}
library(multinma)
options(mc.cores = parallel::detectCores())
```

This vignette describes the analysis of data on the mean off-time reduction in patients given dopamine agonists as adjunct therapy in Parkinson's disease, in a network of 7 trials of 4 active drugs plus placebo [@TSD2].
The data are available in this package as `parkinsons`:
```{r}
head(parkinsons)
```

We consider analysing these data in three separate ways:

1. Using arm-based data (means `y` and corresponding standard errors `se`);
2. Using contrast-based data (mean differences `diff` and corresponding standard errors `se_diff`);
3. A combination of the two, where some studies contribute arm-based data, and other contribute contrast-based data.

***

**Note:** In this case, with Normal likelihoods for both arms and contrasts, we will see that the three analyses give identical results.
In general, unless the arm-based likelihood is Normal, results from a model using a contrast-based likelihood will not exactly match those from a model using an arm-based likelihood, since the contrast-based Normal likelihood is only an approximation.
Similarity of results depends on the suitability of the Normal approximation, which may not always be appropriate - e.g. with a small number of events or small sample size for a binary outcome.
The use of an arm-based likelihood (sometimes called an "exact" likelihood) is therefore preferable where possible in general.

***

## Analysis of arm-based data
We begin with an analysis of the arm-based data - means and standard errors.

### Setting up the network
We have arm-level continuous data giving the mean off-time reduction (`y`) and standard error (`se`) in each arm.
We use the function `set_agd_arm()` to set up the network.
```{r}
arm_net <- set_agd_arm(parkinsons, 
                      study = studyn,
                      trt = trtn,
                      y = y, 
                      se = se,
                      sample_size = n,
                      trt_ref = 1)
arm_net
```

The `sample_size` argument is optional, but enables the nodes to be weighted by sample size in the network plot.

Plot the network structure.
```{r parkinsons_network_plot}
plot(arm_net, weight_edges = TRUE, weight_nodes = TRUE)
```

### Meta-analysis models
We fit both fixed effect (FE) and random effects (RE) models.

#### Fixed effect meta-analysis
First, we fit a fixed effect model using the `nma()` function with `trt_effects = "fixed"`.
We use $\mathrm{N}(0, 10^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 10))
```

The model is fitted using the `nma()` function.
We specify that a cloglog link will be used with `link = "cloglog"` (the Binomial likelihood is the default for these data), and specify the log follow-up time offset using the regression formula `regression = ~offset(log(time))`.
```{r}
arm_fit_FE <- nma(arm_net, 
                  trt_effects = "fixed",
                  prior_intercept = normal(scale = 10),
                  prior_trt = normal(scale = 10))
```

Basic paramter summaries are given by the `print()` method:
```{r}
arm_fit_FE
```

By default, summaries of the study-specific intercepts $\mu_j$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(arm_fit_FE, pars = c("d", "mu"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r arm_FE_pp_plot}
plot_prior_posterior(arm_fit_FE)
```

#### Random effects meta-analysis
We now fit a random effects model using the `nma()` function with `trt_effects = "random"`.
Again, we use $\mathrm{N}(0, 10^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and we additionally use a $\mathrm{half-N}(5^2)$ prior for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 10))
summary(half_normal(scale = 5))
```

Fitting the RE model
```{r, warning=FALSE}
arm_fit_RE <- nma(arm_net, 
                  trt_effects = "random",
                  prior_intercept = normal(scale = 10),
                  prior_trt = normal(scale = 10),
                  prior_het = half_normal(scale = 5))
```

Basic paramter summaries are given by the `print()` method:
```{r}
arm_fit_RE
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(arm_fit_FE, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r arm_RE_pp_plot}
plot_prior_posterior(arm_fit_RE)
```


#### Model comparison
Model fit can be checked using the `dic()` function:
```{r}
(dic_FE <- dic(arm_fit_FE))
```
```{r}
(dic_RE <- dic(arm_fit_RE))
```

Both models fit the data well, having posterior mean residual deviance close to the number of data points.
The DIC is similar between models, so we choose the FE model based on parsimony.

We can also examine the residual deviance contributions with the corresponding `plot()` method.
```{r arm_FE_resdev_plot}
plot(dic_FE)
```

```{r arm_RE_resdev_plot}
plot(dic_RE)
```


### Further results
Following @TSD2, we produce absolute predictions of the mean off-time reduction on each treatment assuming a Normal distribution for the outcomes on treatment 1 (placebo) with mean $-4.2$ and precision $1.11$.
We use the `predict()` method, where the `baseline` argument takes a `distr()` distribution object with which we specify the corresponding Normal distribution.
```{r arm_pred_FE, fig.height = 2}
arm_pred_FE <- predict(arm_fit_FE, 
                       newdata = data.frame(time = 3),
                       baseline = distr(qnorm, mean = -4.2, sd = 1.11^-0.5),
                       type = "response")
arm_pred_FE
plot(arm_pred_FE)
```
```{r arm_pred_RE, fig.height = 2}
arm_pred_RE <- predict(arm_fit_RE, 
                       newdata = data.frame(time = 3),
                       baseline = distr(qnorm, mean = -4.2, sd = 1.11^-0.5),
                       type = "response")
arm_pred_RE
plot(arm_pred_RE)
```

If the `baseline` argument is ommitted, predictions of mean off-time reduction will be produced for every study in the network based on their estimated baseline response on placebo $\mu_j$:
```{r arm_pred_RE_all, fig.height=8}
arm_pred_FE_studies <- predict(arm_fit_FE, type = "response")
arm_pred_FE_studies
plot(arm_pred_FE_studies)
```

We can also produce treatment rankings, rank probabilities, and cumulative rank probabilities.
```{r parkinsons_ranks, fig.height=2}
(arm_ranks <- posterior_ranks(arm_fit_FE))
plot(arm_ranks)
```
```{r parkinsons_rankprobs}
(arm_rankprobs <- posterior_rank_probs(arm_fit_FE))
plot(arm_rankprobs)
```
```{r parkinsons_cumrankprobs}
(arm_cumrankprobs <- posterior_rank_probs(arm_fit_FE, cumulative = TRUE))
plot(arm_cumrankprobs)
```

## References
