---
title: "Example: Certolizumab"
output: rmarkdown::html_vignette
link-citations: yes
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---

```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```
```{r, include=FALSE}
set.seed(76441)
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```
```{r}
library(dplyr)
library(ggplot2)
```

This vignette describes the analysis of 12 trials comparing 6 treatments against placebo for "the treatment of rheumatoid arthritis (RA)
in patients who had failed on disease-modifying anti-rheumatic drugs (DMARDs)" [@TSD3].
The data are available in this package as `certolizumab`:
```{r}
head(certolizumab)
```

@TSD3 used this data to demonstrate baseline risk meta-regression models.
Plotting the baseline risk against the treatment effect, we suspect there might be an effect of the baseline risk on the treatment effect.
Specifically, the log baseline odds (placebo in this case) seem to be negatively linearly correlated with the odds ratio.
```{r certolizumab_baseline_risk_plot}
certolizumab <-
  certolizumab %>%
  mutate(
    probability = r / n,
    odds = probability / (1 - probability),
    log_odds = log(odds)
  )

p_baseline_risk <-
  left_join(
    filter(certolizumab, trt != "Placebo"),
    filter(certolizumab, trt == "Placebo"),
    by = "study",
    suffix = c("", "_baseline")
  ) %>%
  mutate(log_odds_ratio = log_odds - log_odds_baseline, n_total = n + n_baseline) %>%
  ggplot(aes(log_odds_baseline)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  labs(x = "Placebo log odds", y = "log Odds Ratio", size = "Sample Size") +
  theme_multinma()

p_baseline_risk +
  geom_point(aes(y = log_odds_ratio, size = n_total))
```

## Setting up the network
We begin by setting up the network.
```{r}
cert_net <- set_agd_arm(certolizumab,
                        study = study, trt = trt, n = n, r = r,
                        trt_class = dplyr::if_else(trt == "Placebo", "Placebo", "Treatment"))
cert_net
```

Plot the network structure.
```{r, eval=FALSE}
plot(cert_net, weight_edges = TRUE, weight_nodes = TRUE)
```
```{r certolizumab_network_plot, echo=FALSE}
plot(cert_net, weight_edges = TRUE, weight_nodes = TRUE) +
  ggplot2::theme(legend.box.margin = ggplot2::unit(c(0, 0, 0, 4), "lines"))
```

## Meta-analysis models
We fit both fixed effect (FE) and random effects (RE) models.
The special variable `.mu` is used in the `regression` formula to specify a baseline risk meta-regression model.

### Fixed effect meta-analysis
```{r}
cert_fit_FE <- nma(cert_net,
                   trt_effects = "fixed",
                   regression = ~.mu:.trt,
                   prior_intercept = normal(scale = sqrt(1000)),
                   prior_trt = normal(scale = 100),
                   prior_reg = normal(scale = 100),
                   iter = 4000,
                   adapt_delta = 0.95)
```

Basic parameter summaries are given by the `print()` method:
```{r}
cert_fit_FE
```

### Random effects meta-analysis
```{r}
cert_fit_RE <- nma(cert_net,
                   trt_effects = "random",
                   regression = ~.mu:.trt,
                   prior_intercept = normal(scale = sqrt(1000)),
                   prior_trt = normal(scale = 100),
                   prior_reg = normal(scale = 100),
                   iter = 8000,
                   adapt_delta = 0.98)
```

Basic parameter summaries are given by the `print()` method:
```{r}
cert_fit_RE
```

### Model comparison
Model fit can be checked using the `dic()` function:
```{r}
(dic_FE <- dic(cert_fit_FE))
(dic_RE <- dic(cert_fit_RE))
```

We can also examine the residual deviance contributions with the corresponding `plot()` method.
```{r}
plot(dic_FE)
```

```{r}
plot(dic_RE)
```

### Baseline risk meta-regression
Plotting the estimated baseline risk effect (fixed effect model) together with the crude odds ratios.
```{r certolizumab_reg_plot}
cert_mu_reg <-
  cert_fit_FE %>%
  relative_effects(
    newdata = tibble(.mu = seq(log(0.02), log(0.5), length.out = 20)),
    study = .mu
  ) %>%
  as_tibble() %>%
  mutate(
    trt = .trtb,
    log_odds_baseline = as.numeric(as.character(.study))
  )

p_baseline_risk +
  facet_wrap(vars(trt)) +
  geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), data = cert_mu_reg,
              fill = "darkred", alpha = 0.3) +
  geom_line(aes(y = mean), data = cert_mu_reg,
            colour = "darkred") +
  geom_point(aes(y = log_odds_ratio, size = n_total), alpha = 0.6)
```

## Further results
```{r}
newdata <- data.frame(.mu = cert_fit_FE$xbar[[".mu"]])
```
For comparison with @TSD3, we can produce relative effects against "Placebo" using the `relative_effects()` function:
```{r certolizumab_releff_FE, fig.height=3}
(cert_releff_FE <- relative_effects(cert_fit_FE, newdata = newdata))
plot(cert_releff_FE, ref_line = 0)
```
```{r certolizumab_releff_RE, fig.height=3}
(cert_releff_RE <- relative_effects(cert_fit_RE, newdata = newdata))
plot(cert_releff_RE, ref_line = 0)
```

Without `newdata`, `relative_effects()` will produce relative effects per study.
Note that the sampled study-specific intercepts are used.

```{r certolizumab_releff_study_RE}
(cert_releff_study_RE <- relative_effects(cert_fit_RE))
```

`predict()` will use the `.mu` values sampled from the `baseline` distribution.

```{r}
predict(cert_fit_RE, baseline = distr(qnorm, mean = cert_fit_FE$xbar[[".mu"]], sd = 0.5))
```

When not passing a `baseline` distribution, predictions will be produced per study.
The sampled study-specific intercepts are used in the baseline risk meta-regression.

```{r}
predict(cert_fit_RE)
```

We can also produce treatment rankings, rank probabilities, and cumulative rank probabilities.
```{r certolizumab_ranks}
(cert_ranks <- posterior_ranks(cert_fit_RE, newdata = newdata,
                               lower_better = FALSE))
plot(cert_ranks)
```
```{r certolizumab_rankprobs}
(cert_rankprobs <- posterior_rank_probs(cert_fit_RE, newdata = newdata,
                                        lower_better = FALSE))
plot(cert_rankprobs)
```
```{r certolizumab_cumrankprobs}
(cert_cumrankprobs <- posterior_rank_probs(cert_fit_RE, cumulative = TRUE,
                                           newdata = newdata, lower_better = FALSE))
plot(cert_cumrankprobs)
```


It is also possible to combine baseline risk meta-regression with regular meta-regression.
For example, we can add `disease_duration` to the regression formula.
```{r}
nma(cert_net,
    trt_effects = "fixed",
    regression = ~(disease_duration + .mu):.trt,
    prior_intercept = normal(scale = sqrt(1000)),
    prior_trt = normal(scale = 100),
    prior_reg = normal(scale = 100),
    adapt_delta = 0.95)
```

## References

```{r certolizumab_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 3 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# FE Relative effects
tsd_FE <- tribble(
~trt          , ~mean, ~sd , ~lower, ~upper,
"CZP"         , 1.85 , 0.10, 1.67  , 2.06  ,
"Adalimumab"  , 2.13 , 0.11, 1.90  , 2.35  ,
"Etanercept"  , 2.08 , 0.34, 1.47  , 2.80  ,
"Infliximab"  , 1.68 , 0.10, 1.49  , 1.86  ,
"Rituximab"   , 0.36 , 0.50, -0.72 , 1.27  ,
"Tocilizumab" , 2.20 , 0.14, 1.93  , 2.46  ,
) %>%
  arrange(ordered(trt, levels = levels(cert_net$treatments)))

cert_releff_FE <- as.data.frame(cert_releff_FE)

test_that("FE relative effects", {
  expect_equivalent(cert_releff_FE$mean, tsd_FE$mean, tolerance = tol)
  expect_equivalent(cert_releff_FE$sd, tsd_FE$sd, tolerance = tol)
  expect_equivalent(cert_releff_FE$`2.5%`, tsd_FE$lower, tolerance = tol)
  expect_equivalent(cert_releff_FE$`97.5%`, tsd_FE$upper, tolerance = tol)
})

# RE Relative effects
tsd_RE <- tribble(
~trt          , ~mean, ~sd , ~lower, ~upper,
"CZP"         , 1.83 , 0.24, 1.35  , 2.29  ,
"Adalimumab"  , 2.18 , 0.22, 1.79  , 2.63  ,
"Etanercept"  , 2.04 , 0.46, 1.19  , 2.94  ,
"Infliximab"  , 1.71 , 0.22, 1.30  , 2.16  ,
"Rituximab"   , 0.37 , 0.59, -0.86 , 1.45  ,
"Tocilizumab" , 2.25 , 0.27, 1.75  , 2.79  ,
) %>%
  arrange(ordered(trt, levels = levels(cert_net$treatments)))

cert_releff_RE <- as.data.frame(cert_releff_RE)

test_that("RE relative effects", {
  expect_equivalent(cert_releff_RE$mean, tsd_RE$mean, tolerance = tol)
  expect_equivalent(cert_releff_RE$sd, tsd_RE$sd, tolerance = tol)
  expect_equivalent(cert_releff_RE$`2.5%`, tsd_RE$lower, tolerance = tol)
  expect_equivalent(cert_releff_RE$`97.5%`, tsd_RE$upper, tolerance = tol)
})

cert_fit_RE_mu <- summary(cert_fit_RE, pars = "mu")
test_that("mean study-specific intercepts identical to those in parameter summary", {
  expect_equal(cert_releff_study_RE$studies$.mu, unname(cert_fit_RE_mu$summary$mean))
})

# Heterogeneity SD
cert_tau <- as.data.frame(summary(cert_fit_RE, pars = "tau"))

test_that("RE heterogeneity SD", {
  expect_equivalent(cert_tau$mean, 0.19, tolerance = tol)
  expect_equivalent(cert_tau$sd, 0.19, tolerance = tol)
  expect_equivalent(cert_tau$`2.5%`, 0.01, tolerance = tol)
  expect_equivalent(cert_tau$`97.5%`, 0.70, tolerance = tol)
})

# Baseline risk meta-regression
expect_equal(cert_fit_FE$xbar[[".mu"]], -2.421, tolerance = 0.01)
expect_equal(cert_fit_RE$xbar[[".mu"]], -2.421, tolerance = 0.01)

cert_beta_FE <- as.data.frame(summary(cert_fit_FE, pars = "beta"))

test_that("FE baseline risk meta-regression", {
  expect_equal(cert_beta_FE$mean, -0.93, tolerance = tol)
  expect_equal(cert_beta_FE$sd, 0.09, tolerance = tol)
  expect_equal(cert_beta_FE$`2.5%`, -1.03, tolerance = tol)
  expect_equal(cert_beta_FE$`97.5%`, -0.69, tolerance = tol)
})

cert_beta_RE <- as.data.frame(summary(cert_fit_RE, pars = "beta"))

test_that("RE baseline risk meta-regression", {
  expect_equal(cert_beta_RE$mean, -0.95, tolerance = tol)
  expect_equal(cert_beta_RE$sd, 0.10, tolerance = tol)
  expect_equal(cert_beta_RE$`2.5%`, -1.10, tolerance = tol)
  expect_equal(cert_beta_RE$`97.5%`, -0.70, tolerance = tol)
})

# DIC
test_that("FE DIC", {
  expect_equivalent(dic_FE$resdev, 27.3, tolerance = tol_dic)
  expect_equivalent(dic_FE$pd, 19.0, tolerance = tol_dic)
  expect_equivalent(dic_FE$dic, 46.3, tolerance = tol_dic)
})

test_that("RE DIC", {
  expect_equivalent(dic_RE$resdev, 24.2, tolerance = tol_dic)
  expect_equivalent(dic_RE$pd, 19.4, tolerance = tol_dic)
  expect_equivalent(dic_RE$dic, 43.6, tolerance = tol_dic)
})
```
