---
title: "Example: Atrial fibrillation"
output: rmarkdown::html_vignette
link-citations: yes
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---


```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```
```{r, include=FALSE}
set.seed(4783982)
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

This vignette describes the analysis of 26 trials comparing 17 treatments in 4 classes for the prevention of stroke in patients with atrial fibrillation [@Cooper2009].
The data are available in this package as `atrial_fibrillation`:
```{r}
head(atrial_fibrillation)
```

@Cooper2009 used this data to demonstrate meta-regression models, which we recreate here.

## Setting up the network
Whilst we have data on the patient-years at risk in each study (`E`), we ignore this here to follow the analysis of @Cooper2009, instead analysing the number of patients with stroke (`r`) out of the total (`n`) in each arm.
We use the function `set_agd_arm()` to set up the network, making sure to specify the treatment classes `trt_class`.
We remove the WASPO study from the network as both arms had zero events, and this study therefore contributes no information.
```{r}
af_net <- set_agd_arm(atrial_fibrillation[atrial_fibrillation$studyc != "WASPO", ], 
                      study = studyc,
                      trt = trtc,
                      r = r, 
                      n = n,
                      trt_class = trt_class)
af_net
```

(A better analysis, accounting for differences in the patient-years at risk between studies, can be performed by specifying a rate outcome with `r` and `E` in `set_agd_arm()` above.
The following code remains identical.)

Plot the network with the `plot()` method:
```{r af_network_plot, fig.width=8, fig.height=6, out.width="100%"}
plot(af_net, weight_nodes = TRUE, weight_edges = TRUE, show_trt_class = TRUE) + 
  ggplot2::theme(legend.position = "bottom", legend.box = "vertical")
```


## Meta-analysis models
We fit two (random effects) models:

1. A standard NMA model without any covariates (model 1 of @Cooper2009);
2. A meta-regression model adjusting for the proportion of individuals in each study with prior stroke, with shared interaction coefficients by treatment class (model 4b of @Cooper2009).

### NMA with no covariates
We fit a random effects model using the `nma()` function with `trt_effects = "random"`.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and a $\textrm{half-N}(5^2)$ prior for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
summary(half_normal(scale = 5))
```

Fitting the model with the `nma()` function. We increase the target acceptance rate `adapt_delta = 0.99` to minimise divergent transition warnings.
```{r, eval=FALSE}
af_fit_1 <- nma(af_net, 
                trt_effects = "random",
                prior_intercept = normal(scale = 100),
                prior_trt = normal(scale = 100),
                prior_het = half_normal(scale = 5),
                adapt_delta = 0.99)
```
```{r, echo=FALSE}
af_fit_1 <- nma(af_net, 
                seed = 103533305,
                trt_effects = "random",
                prior_intercept = normal(scale = 100),
                prior_trt = normal(scale = 100),
                prior_het = half_normal(scale = 5),
                adapt_delta = 0.99,
                iter = 5000)
```

Basic parameter summaries are given by the `print()` method:
```{r}
af_fit_1
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(af_fit_1, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r af_1_pp_plot, fig.width=8, fig.height=6, out.width="100%"}
plot_prior_posterior(af_fit_1, prior = c("trt", "het"))
```

We can compute relative effects against placebo/standard care with the `relative_effects()` function with the `trt_ref` argument:
```{r}
(af_1_releff <- relative_effects(af_fit_1, trt_ref = "Placebo/Standard care"))
```

These estimates can easily be plotted with the `plot()` method:
```{r af_1_releff_plot}
plot(af_1_releff, ref_line = 0)
```

We can also produce treatment rankings, rank probabilities, and cumulative rank probabilities.
```{r af_1_ranks}
(af_1_ranks <- posterior_ranks(af_fit_1))
plot(af_1_ranks)
```
```{r af_1_rankprobs}
(af_1_rankprobs <- posterior_rank_probs(af_fit_1))
plot(af_1_rankprobs)
```
```{r af_1_cumrankprobs}
(af_1_cumrankprobs <- posterior_rank_probs(af_fit_1, cumulative = TRUE))
plot(af_1_cumrankprobs)
```

### Network meta-regression adjusting for proportion of prior stroke
We now consider a meta-regression model adjusting for the proportion of individuals in each study with prior stroke, with shared interaction coefficients by treatment class.
The regression model is specified in the `nma()` function using a formula in the `regression` argument.
The formula `~ .trt:stroke` means that interactions of prior stroke with treatment will be included; the `.trt` special variable indicates treatment, and `stroke` is in the original data set.
We specify `class_interactions = "common"` to denote that the interaction parameters are to be common (i.e. shared) between treatments within each class.
(Setting `class_interactions = "independent"` would fit model 2 of @Cooper2009 with separate interactions for each treatment, data permitting.)
We use the same prior distributions as above, but additionally require a prior distribution for the regression coefficients `prior_reg`; we use a $\mathrm{N}(0, 100^2)$ prior distribution.
The [QR decomposition](https://mc-stan.org/users/documentation/case-studies/qr_regression.html) can greatly improve the efficiency of sampling for regression models by decorrelating the sampling space; we specify that this should be used with `QR = TRUE`, and increase the target acceptance rate `adapt_delta = 0.99` to minimise divergent transition warnings.
```{r, eval=FALSE}
af_fit_4b <- nma(af_net, 
                 trt_effects = "random",
                 regression = ~ .trt:stroke,
                 class_interactions = "common",
                 QR = TRUE,
                 prior_intercept = normal(scale = 100),
                 prior_trt = normal(scale = 100),
                 prior_reg = normal(scale = 100),
                 prior_het = half_normal(scale = 5),
                 adapt_delta = 0.99)
```
```{r, echo=FALSE, eval=!params$run_tests}
af_fit_4b <- nma(af_net, 
                 seed = 579212814,
                 trt_effects = "random",
                 regression = ~ .trt:stroke,
                 class_interactions = "common",
                 QR = TRUE,
                 prior_intercept = normal(scale = 100),
                 prior_trt = normal(scale = 100),
                 prior_reg = normal(scale = 100),
                 prior_het = half_normal(scale = 5),
                 adapt_delta = 0.99)
```
```{r, echo=FALSE, eval=params$run_tests}
af_fit_4b <- nowarn_on_ci(nma(af_net, 
                 seed = 579212814,
                 trt_effects = "random",
                 regression = ~ .trt:stroke,
                 class_interactions = "common",
                 QR = TRUE,
                 prior_intercept = normal(scale = 100),
                 prior_trt = normal(scale = 100),
                 prior_reg = normal(scale = 100),
                 prior_het = half_normal(scale = 5),
                 adapt_delta = 0.99,
                 iter = 5000))
```

Basic parameter summaries are given by the `print()` method:
```{r}
af_fit_4b
```

The estimated treatment effects `d[]` shown here correspond to relative effects at the reference level of the covariate, here proportion of prior stroke centered at the network mean value 0.296.

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(af_fit_4b, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r af_4b_pp_plot}
plot_prior_posterior(af_fit_4b, prior = c("reg", "het"))
```

We can compute relative effects against placebo/standard care with the `relative_effects()` function with the `trt_ref` argument, which by default produces relative effects for the observed proportions of prior stroke in each study:
```{r af_4b_releff_plot, fig.height = 16, eval=FALSE}
# Not run
(af_4b_releff <- relative_effects(af_fit_4b, trt_ref = "Placebo/Standard care"))
plot(af_4b_releff, ref_line = 0)
```

We can produce estimated treatment effects for particular covariate values using the `newdata` argument.
For example, treatment effects when no individuals or all individuals have prior stroke are produced by
```{r af_4b_releff_01_plot}
(af_4b_releff_01 <- relative_effects(af_fit_4b, 
                                     trt_ref = "Placebo/Standard care",
                                     newdata = data.frame(stroke = c(0, 1), 
                                                          label = c("stroke = 0", "stroke = 1")),
                                     study = label))
plot(af_4b_releff_01, ref_line = 0)
```


The estimated class interactions (against the reference "Mixed" class) are very uncertain.
```{r af_4b_betas}
plot(af_fit_4b, pars = "beta", stat = "halfeye", ref_line = 0)
```

The interactions are more straightforward to interpret if we transform the interaction coefficients (using the consistency equations) so that they are against the control class:
```{r af_4b_betas_transformed}
af_4b_beta <- as.array(af_fit_4b, pars = "beta")

# Subtract beta[Control:stroke] from the other class interactions
af_4b_beta[ , , 2:3] <- sweep(af_4b_beta[ , , 2:3], 1:2, 
                              af_4b_beta[ , , "beta[.trtclassControl:stroke]"], FUN = "-")

# Set beta[Anti-coagulant:stroke] = -beta[Control:stroke]
af_4b_beta[ , , "beta[.trtclassControl:stroke]"] <- -af_4b_beta[ , , "beta[.trtclassControl:stroke]"]
names(af_4b_beta)[1] <- "beta[.trtclassAnti-coagulant:stroke]"

# Summarise
summary(af_4b_beta)
plot(summary(af_4b_beta), stat = "halfeye", ref_line = 0)
```

There is some evidence that the effect of anti-coagulants increases (compared to control) with prior stroke.
There is little evidence the effect of anti-platelets reduces with prior stroke, although the point estimate represents a substantial reduction in effectiveness, and the 95% Credible Interval includes values that correspond to substantial increases in treatment effect.
The interaction effect of stroke on mixed treatments is very uncertain, but potentially indicates a substantial reduction in treatment effects with prior stroke.

We can also produce treatment rankings, rank probabilities, and cumulative rank probabilities.
By default (without the `newdata` argument specified), these are produced at the value of `stroke` for each study in the network in turn.
To instead produce rankings for when no individuals or all individuals have prior stroke, we specify the `newdata` argument.
```{r af_4b_ranks}
(af_4b_ranks <- posterior_ranks(af_fit_4b,
                                newdata = data.frame(stroke = c(0, 1), 
                                                     label = c("stroke = 0", "stroke = 1")), 
                                study = label))
plot(af_4b_ranks)
```
```{r af_4b_rankprobs, fig.height=12}
(af_4b_rankprobs <- posterior_rank_probs(af_fit_4b,
                                         newdata = data.frame(stroke = c(0, 1), 
                                                              label = c("stroke = 0", "stroke = 1")), 
                                         study = label))

# Modify the default output with ggplot2 functionality
library(ggplot2)
plot(af_4b_rankprobs) + 
  facet_grid(Treatment~Study, labeller = label_wrap_gen(20)) + 
  theme(strip.text.y = element_text(angle = 0))
```
```{r af_4b_cumrankprobs, fig.height=12}
(af_4b_cumrankprobs <- posterior_rank_probs(af_fit_4b, cumulative = TRUE,
                                            newdata = data.frame(stroke = c(0, 1), 
                                                                 label = c("stroke = 0", "stroke = 1")), 
                                            study = label))

plot(af_4b_cumrankprobs) + 
  facet_grid(Treatment~Study, labeller = label_wrap_gen(20)) + 
  theme(strip.text.y = element_text(angle = 0))
```

## Model fit and comparison
Model fit can be checked using the `dic()` function:
```{r}
(af_dic_1 <- dic(af_fit_1))
```
```{r}
(af_dic_4b <- dic(af_fit_4b))
```

Both models fit the data well, having posterior mean residual deviance close to the number of data points.
The DIC is slightly lower for the meta-regression model, although only by a couple of points (substantial differences are usually considered 3-5 points).
The estimated heterogeneity standard deviation is much lower for the meta-regression model, suggesting that adjusting for the proportion of patients with prior stroke is explaining some of the heterogeneity in the data.

We can also examine the residual deviance contributions with the corresponding `plot()` method.
```{r af_1_resdev_plot}
plot(af_dic_1)
```

```{r af_4b_resdev_plot}
plot(af_dic_4b)
```

## References

```{r atrial_fibrillation_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 2 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# No covariates

Cooper_1_releff <- tribble(
~trt                                       , ~est , ~lower, ~upper,
"Low adjusted dose anti-coagulant"         , -1.08,-1.77  , -0.37 ,
"Standard adjusted dose anti-coagulant"    , -0.76,-1.16  , -0.36 ,
"Fixed dose warfarin"                      , 0.18 ,-0.73  , 1.06  ,
"Low dose aspirin"                         , -0.15,-0.56  , 0.27  ,
"Medium dose aspirin"                      , -0.37,-0.83  , 0.07  ,
"High dose aspirin"                        , -0.25,-1.72  , 1.23  ,
"Alternate day aspirin"                    , -1.67,-4.54  , 0.41  ,
"Ximelagatran"                             , -0.84,-1.50  , -0.18 ,
"Triflusal"                                , -0.11,-1.35  , 1.20  ,
"Indobufen"                                , -0.52,-1.47  , 0.47  ,
"Dipyridamole"                             , -0.18,-1.02  , 0.66  ,
"Fixed dose warfarin + low dose aspirin"   , -0.29,-1.09  , 0.51  ,
"Fixed dose warfarin + medium dose aspirin", 0.13 ,-0.60  , 0.83  ,
"Acenocoumarol"                            , -1.56,-3.31  , 0.06  ,
"Low dose aspirin + copidogrel"            , -0.24,-1.06  , 0.57  ,
"Low dose aspirin + dipyridamole"          , -0.49,-1.38  , 0.38  ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(af_net$treatments))) %>%
  arrange(trt)

af_1_releff_df <- as.data.frame(af_1_releff)

test_that("Relative effects (no covariates)", {
  expect_equivalent(af_1_releff_df$mean, Cooper_1_releff$est, tolerance = tol)
  expect_equivalent(af_1_releff_df$`2.5%`, Cooper_1_releff$lower, tolerance = tol)
  expect_equivalent(af_1_releff_df$`97.5%`, Cooper_1_releff$upper, tolerance = tol)
})

af_1_tau <- as.data.frame(summary(af_fit_1, pars = "tau"))

test_that("Heterogeneity SD (no covariates)", {
  expect_equivalent(af_1_tau$`50%`, 0.28, tolerance = tol)
  expect_equivalent(af_1_tau$`2.5%`, 0.02, tolerance = tol)
  expect_equivalent(af_1_tau$`97.5%`, 0.57, tolerance = tol)
})

test_that("DIC (no covariates)", {
  expect_equivalent(af_dic_1$resdev, 60.22, tolerance = tol_dic)
  expect_equivalent(af_dic_1$pd, 48.35, tolerance = tol_dic)
  expect_equivalent(af_dic_1$dic, 108.57, tolerance = tol_dic)
})

test_that("SUCRAs", {
  af_ranks_1 <- posterior_ranks(af_fit_1, sucra = TRUE)
  af_rankprobs_1 <- posterior_rank_probs(af_fit_1, sucra = TRUE)
  af_cumrankprobs_1 <- posterior_rank_probs(af_fit_1, cumulative = TRUE, sucra = TRUE)
  
  expect_equal(af_ranks_1$summary$sucra, af_rankprobs_1$summary$sucra)
  expect_equal(af_ranks_1$summary$sucra, af_cumrankprobs_1$summary$sucra)
})


# Check construction of all contrasts
af_1_releff_all_contr <- relative_effects(af_fit_1, all_contrasts = TRUE)

# Reconstruct from basic contrasts in each study
dk <- function(study, trt, sims) {
  if (trt == "Placebo/Standard care") return(0)
  else if (is.na(study)) {
    return(sims[ , , paste0("d[", trt, "]"), drop = FALSE])
  } else {
    return(sims[ , , paste0("d[", study, ": ", trt, "]"), drop = FALSE])
  }
}

test_af_1_all_contr <- tibble(
  contr = af_1_releff_all_contr$summary$parameter,
  .trtb = factor(stringr::str_extract(contr, "(?<=\\[)(.+)(?= vs\\.)"), levels = levels(af_net$treatments)),
  .trta = factor(stringr::str_extract(contr, "(?<=vs\\. )(.+)(?=\\])"), levels = levels(af_net$treatments))
) %>%
  rowwise() %>%
  mutate(as_tibble(multinma:::summary.mcmc_array(dk(NA, .trtb, af_1_releff$sims) - dk(NA, .trta, af_1_releff$sims)))) %>%
  select(.trtb, .trta, parameter = contr, mean:Rhat)

test_that("Construction of all contrasts is correct (no covariates)", {
  ntrt <- nlevels(af_net$treatments)
  expect_equal(nrow(af_1_releff_all_contr$summary), ntrt * (ntrt - 1) / 2)
  expect_equal(select(af_1_releff_all_contr$summary, -Rhat),
               select(test_af_1_all_contr, -Rhat),
               check.attributes = FALSE)
})

# With stroke covariate, shared interactions

Cooper_4b_releff <- tribble(
~trt                                       , ~est  , ~lower, ~upper, 
"Low adjusted dose anti-coagulant"         , -1.20 ,-1.89  , -0.54 ,
"Standard adjusted dose anti-coagulant"    , -0.77 ,-1.14  , -0.38 ,
"Fixed dose warfarin"                      , -0.11 ,-0.90  , 0.72  ,
"Low dose aspirin"                         , -0.08 ,-0.47  , 0.30  ,
"Medium dose aspirin"                      , -0.45 ,-0.87  , -0.03 ,
"High dose aspirin"                        , -0.39 ,-1.86  , 1.11  ,
"Alternate day aspirin"                    , -1.74 ,-5.16  , 0.48  ,
"Ximelagatran"                             , -0.86 ,-1.42  , -0.27 ,
"Triflusal"                                , 0.13  ,-1.05  , 1.38  ,
"Indobufen"                                , -1.21 ,-2.26  , -0.13 ,
"Dipyridamole"                             , -0.21 ,-1.01  , 0.58  ,
"Fixed dose warfarin + low dose aspirin"   , 0.54  ,-0.80  , 1.85  ,
"Fixed dose warfarin + medium dose aspirin", 0.12  ,-0.53  , 0.80  ,
"Acenocoumarol"                            , -0.534,-2.67  , 1.38  ,
"Low dose aspirin + copidogrel"            , -0.14 ,-0.82  , 0.53  ,
"Low dose aspirin + dipyridamole"          , -0.53 ,-1.38  , 0.30  ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(af_net$treatments))) %>%
  arrange(trt)

af_4b_releff_Cooper <- as.data.frame(relative_effects(af_fit_4b, 
                                                      newdata = tibble(stroke = 0.27),
                                                      trt_ref = "Placebo/Standard care"))

test_that("Relative effects (common interaction)", {
  expect_equivalent(af_4b_releff_Cooper$mean, Cooper_4b_releff$est, tolerance = tol)
  expect_equivalent(af_4b_releff_Cooper$`2.5%`, Cooper_4b_releff$lower, tolerance = tol)
  expect_equivalent(af_4b_releff_Cooper$`97.5%`, Cooper_4b_releff$upper, tolerance = tol)
})

Cooper_4b_beta <- tribble(
~trt_class       , ~est , ~lower, ~upper,
"Anti-coagulant", -0.71,-1.58  , 0.15  ,
"Anti-platelet" , 0.23 ,-0.45  , 0.93  ,
#"Mixed"          , 3.05 ,-1.26  , 7.30  ,
"Mixed"          , 3.21 ,-0.91  , 7.30  ,
)

af_4b_beta_df <- as.data.frame(summary(af_4b_beta))

test_that("Interaction estimates (common interaction)", {
  expect_equivalent(af_4b_beta_df$mean, Cooper_4b_beta$est, tolerance = tol)
  skip_on_ci()
  expect_equivalent(af_4b_beta_df$`2.5%`, Cooper_4b_beta$lower, tolerance = tol)
  expect_equivalent(af_4b_beta_df$`97.5%`, Cooper_4b_beta$upper, tolerance = tol)
})

af_4b_tau <- as.data.frame(summary(af_fit_4b, pars = "tau"))

test_that("Heterogeneity SD (common interaction)", {
  expect_equivalent(af_4b_tau$`50%`, 0.19, tolerance = tol)
  expect_equivalent(af_4b_tau$`2.5%`, 0.01, tolerance = tol)
  expect_equivalent(af_4b_tau$`97.5%`, 0.48, tolerance = tol)
})

test_that("DIC (common interaction)", {
  expect_equivalent(af_dic_4b$resdev, 58.74, tolerance = tol_dic)
  expect_equivalent(af_dic_4b$pd, 48.25, tolerance = tol_dic)
  expect_equivalent(af_dic_4b$dic, 106.99, tolerance = tol_dic)
})

test_that("SUCRAs", {
  stroke_01 <- data.frame(stroke = c(0, 1), label = c("stroke = 0", "stroke = 1"))
  af_ranks_4b <- posterior_ranks(af_fit_4b, newdata = stroke_01, 
                                study = label, sucra = TRUE)
  af_rankprobs_4b <- posterior_rank_probs(af_fit_4b, newdata = stroke_01, 
                                           study = label, sucra = TRUE)
  af_cumrankprobs_4b <- posterior_rank_probs(af_fit_4b, cumulative = TRUE, newdata = stroke_01,
                                              study = label, sucra = TRUE)
  
  expect_equal(af_ranks_4b$summary$sucra, af_rankprobs_4b$summary$sucra)
  expect_equal(af_ranks_4b$summary$sucra, af_cumrankprobs_4b$summary$sucra)
})

# Check construction of all contrasts
af_4b_releff <- relative_effects(af_fit_4b, trt_ref = "Placebo/Standard care")
af_4b_releff_all_contr <- relative_effects(af_fit_4b, all_contrasts = TRUE)

test_af_4b_all_contr <- tibble(
  contr = af_4b_releff_all_contr$summary$parameter,
  .study = factor(stringr::str_extract(contr, "(?<=\\[)(.+)(?=:)")),
  .trtb = factor(stringr::str_extract(contr, "(?<=\\: )(.+)(?= vs\\.)"), levels = levels(af_net$treatments)),
  .trta = factor(stringr::str_extract(contr, "(?<=vs\\. )(.+)(?=\\])"), levels = levels(af_net$treatments))
) %>% 
  rowwise() %>% 
  mutate(as_tibble(multinma:::summary.mcmc_array(dk(.study, .trtb, af_4b_releff$sims) - dk(.study, .trta, af_4b_releff$sims)))) %>% 
  select(.study, .trtb, .trta, parameter = contr, mean:Rhat)

test_that("Construction of all contrasts is correct (common interaction)", {
  ntrt <- nlevels(af_net$treatments)
  nstudy <- nlevels(test_af_4b_all_contr$.study)
  expect_equal(nrow(af_4b_releff_all_contr$summary), nstudy * ntrt * (ntrt - 1) / 2)
  expect_equal(select(af_4b_releff_all_contr$summary, -Rhat), 
               select(test_af_4b_all_contr, -Rhat), 
               check.attributes = FALSE)
})

# Check construction of all contrasts in target population
af_4b_releff_new <- relative_effects(af_fit_4b, newdata = tibble(stroke = 0.27), trt_ref = "Placebo/Standard care")
af_4b_releff_all_contr_new <- relative_effects(af_fit_4b, newdata = tibble(stroke = 0.27), all_contrasts = TRUE)

test_af_4b_all_contr_new <- tibble(
  contr = af_4b_releff_all_contr_new$summary$parameter,
  .study = factor(stringr::str_extract(contr, "(?<=\\[)(.+)(?=:)")),
  .trtb = factor(stringr::str_extract(contr, "(?<=\\: )(.+)(?= vs\\.)"), levels = levels(af_net$treatments)),
  .trta = factor(stringr::str_extract(contr, "(?<=vs\\. )(.+)(?=\\])"), levels = levels(af_net$treatments))
) %>% 
  rowwise() %>% 
  mutate(as_tibble(multinma:::summary.mcmc_array(dk(.study, .trtb, af_4b_releff_new$sims) - dk(.study, .trta, af_4b_releff_new$sims)))) %>% 
  select(.study, .trtb, .trta, parameter = contr, mean:Rhat)

test_that("Construction of all contrasts in target population is correct (common interaction)", {
  ntrt <- nlevels(af_net$treatments)
  nstudy <- nlevels(test_af_4b_all_contr_new$.study)
  expect_equal(nrow(af_4b_releff_all_contr_new$summary), nstudy * ntrt * (ntrt - 1) / 2)
  expect_equal(select(af_4b_releff_all_contr_new$summary, -Rhat), 
               select(test_af_4b_all_contr_new, -Rhat), 
               check.attributes = FALSE)
})

test_that("Robust to custom options(contrasts) settings", {
  af_fit_4b_SAS <- withr::with_options(list(contrasts = c(ordered = "contr.SAS",
                                                       unordered = "contr.SAS")),
             nowarn_on_ci(nma(af_net, 
                 seed = 579212814,
                 trt_effects = "random",
                 regression = ~ .trt:stroke,
                 class_interactions = "common",
                 QR = TRUE,
                 prior_intercept = normal(scale = 100),
                 prior_trt = normal(scale = 100),
                 prior_reg = normal(scale = 100),
                 prior_het = half_normal(scale = 5),
                 adapt_delta = 0.99,
                 iter = 5000)))

  expect_equal(as_tibble(summary(af_fit_4b_SAS))[, c("parameter", "mean", "sd")],
               as_tibble(summary(af_fit_4b))[, c("parameter", "mean", "sd")],
               tolerance = tol)
  expect_equal(as_tibble(relative_effects(af_fit_4b_SAS))[, c("parameter", "mean", "sd")],
               as_tibble(relative_effects(af_fit_4b))[, c("parameter", "mean", "sd")],
               tolerance = tol)
})

```
