---
title: "Example: Dietary fat"
output: rmarkdown::html_vignette
link-citations: yes
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---


```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

This vignette describes the analysis of 10 trials comparing reduced fat diets to control (non-reduced fat diets) for preventing mortality [@Hooper2000; @TSD2].
The data are available in this package as `dietary_fat`:
```{r}
head(dietary_fat)
```


## Setting up the network
We begin by setting up the network - here just a pairwise meta-analysis.
We have arm-level rate data giving the number of deaths (`r`) and the person-years at risk (`E`) in each arm, so we use the function `set_agd_arm()`.
We set "Control" as the reference treatment.
```{r}
diet_net <- set_agd_arm(dietary_fat, 
                        study = studyc,
                        trt = trtc,
                        r = r, 
                        E = E,
                        trt_ref = "Control",
                        sample_size = n)
diet_net
```

We also specify the optional `sample_size` argument, although it is not strictly necessary here.
In this case `sample_size` would only be required to produce a network plot with nodes weighted by sample size, and a network plot is not particularly informative for a meta-analysis of only two treatments.
(The `sample_size` argument is more important when a regression model is specified, since it also enables automatic centering of predictors and production of predictions for studies in the network, see `?set_agd_arm`.)

## Meta-analysis models
We fit both fixed effect (FE) and random effects (RE) models.

### Fixed effect meta-analysis
First, we fit a fixed effect model using the `nma()` function with `trt_effects = "fixed"`.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
```

The model is fitted using the `nma()` function.
By default, this will use a Poisson likelihood with a log link function, auto-detected from the data.
```{r}
diet_fit_FE <- nma(diet_net, 
                   trt_effects = "fixed",
                   prior_intercept = normal(scale = 100),
                   prior_trt = normal(scale = 100))
```

Basic parameter summaries are given by the `print()` method:
```{r}
diet_fit_FE
```

By default, summaries of the study-specific intercepts $\mu_j$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(diet_fit_FE, pars = c("d", "mu"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r diet_FE_pp_plot}
plot_prior_posterior(diet_fit_FE)
```

### Random effects meta-analysis
We now fit a random effects model using the `nma()` function with `trt_effects = "random"`.
Again, we use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and we additionally use a $\textrm{half-N}(5^2)$ prior for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
summary(half_normal(scale = 5))
```

Fitting the RE model
```{r, eval=FALSE}
diet_fit_RE <- nma(diet_net, 
                   trt_effects = "random",
                   prior_intercept = normal(scale = 100),
                   prior_trt = normal(scale = 100),
                   prior_het = half_normal(scale = 5))
```
```{r, echo=FALSE, warning=FALSE}
diet_fit_RE <- nowarn_on_ci(
                 nma(diet_net, 
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = half_normal(scale = 5))
                 )
```

Basic parameter summaries are given by the `print()` method:
```{r}
diet_fit_RE
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(diet_fit_RE, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r diet_RE_pp_plot}
plot_prior_posterior(diet_fit_RE, prior = c("trt", "het"))
```


### Model comparison
Model fit can be checked using the `dic()` function:
```{r}
(dic_FE <- dic(diet_fit_FE))
```
```{r}
(dic_RE <- dic(diet_fit_RE))
```

Both models appear to fit the data well, as the residual deviance is close to the number of data points.
The DIC is very similar between models, so the FE model may be preferred for parsimony.

We can also examine the residual deviance contributions with the corresponding `plot()` method.
```{r diet_FE_resdev_plot}
plot(dic_FE)
```

```{r diet_RE_resdev_plot}
plot(dic_RE)
```


## Further results
@TSD2 produce absolute predictions of the mortality rates on reduced fat and control diets, assuming a Normal distribution on the baseline log rate of mortality with mean $-3$ and precision $1.77$.
We can replicate these results using the `predict()` method.
The `baseline` argument takes a `distr()` distribution object, with which we specify the corresponding Normal distribution.
We set `type = "response"` to produce predicted rates (`type = "link"` would produce predicted log rates).
```{r diet_pred_FE, fig.height = 2}
pred_FE <- predict(diet_fit_FE, 
                   baseline = distr(qnorm, mean = -3, sd = 1.77^-0.5), 
                   type = "response")
pred_FE
plot(pred_FE)
```
```{r diet_pred_RE, fig.height = 2}
pred_RE <- predict(diet_fit_RE, 
                   baseline = distr(qnorm, mean = -3, sd = 1.77^-0.5), 
                   type = "response")
pred_RE
plot(pred_RE)
```

If the `baseline` argument is omitted, predicted rates will be produced for every study in the network based on their estimated baseline log rate $\mu_j$:
```{r diet_pred_FE_all, fig.height=10}
pred_FE_studies <- predict(diet_fit_FE, type = "response")
pred_FE_studies
plot(pred_FE_studies) + ggplot2::facet_grid(Study~., labeller = ggplot2::label_wrap_gen(width = 10))
```


## References

```{r diet_tests_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 2 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# Relative effects
diet_FE_releff <- as.data.frame(relative_effects(diet_fit_FE))

test_that("FE relative effects", {
  expect_equivalent(diet_FE_releff$mean, -0.01, tolerance = tol)
  expect_equivalent(diet_FE_releff$sd, 0.054, tolerance = tol)
  expect_equivalent(diet_FE_releff$`2.5%`, -0.11, tolerance = tol)
  expect_equivalent(diet_FE_releff$`50%`, -0.01, tolerance = tol)
  expect_equivalent(diet_FE_releff$`97.5%`, 0.10, tolerance = tol)
})

diet_RE_releff <- as.data.frame(relative_effects(diet_fit_RE))

test_that("RE relative effects", {
  expect_equivalent(diet_RE_releff$mean, -0.02, tolerance = tol)
  expect_equivalent(diet_RE_releff$sd, 0.09, tolerance = tol)
  expect_equivalent(diet_RE_releff$`2.5%`, -0.19, tolerance = tol)
  expect_equivalent(diet_RE_releff$`50%`, -0.01, tolerance = tol)
  expect_equivalent(diet_RE_releff$`97.5%`, 0.16, tolerance = tol)
})

# RE heterogeneity SD
diet_RE_sd <- as.data.frame(summary(diet_fit_RE, pars = "tau"))

test_that("RE heterogeneity SD", {
  expect_equivalent(diet_RE_sd$mean, 0.13, tolerance = tol)
  expect_equivalent(diet_RE_sd$sd, 0.12, tolerance = tol)
  expect_equivalent(diet_RE_sd$`2.5%`, 0.00, tolerance = tol)
  expect_equivalent(diet_RE_sd$`50%`, 0.10, tolerance = tol)
  expect_equivalent(diet_RE_sd$`97.5%`, 0.43, tolerance = tol)
})

# DIC
test_that("FE DIC", {
  expect_equivalent(dic_FE$resdev, 23.32, tolerance = tol_dic)
  expect_equivalent(dic_FE$pd, 10.9, tolerance = tol_dic)
  expect_equivalent(dic_FE$dic, 33.2, tolerance = tol_dic)
})

test_that("RE DIC", {
  expect_equivalent(dic_RE$resdev, 21.5, tolerance = tol_dic)
  expect_equivalent(dic_RE$pd, 13.3, tolerance = tol_dic)
  expect_equivalent(dic_RE$dic, 34.8, tolerance = tol_dic)
})

# Predictions
diet_pred_FE <- as.data.frame(pred_FE)

test_that("FE predicted probabilities", {
  expect_equivalent(diet_pred_FE$mean, c(0.06, 0.06), tolerance = tol_dic)
  expect_equivalent(diet_pred_FE$sd, c(0.04, 0.04), tolerance = tol_dic)
  expect_equivalent(diet_pred_FE$`2.5%`, c(0.01, 0.01), tolerance = tol_dic)
  expect_equivalent(diet_pred_FE$`50%`, c(0.05, 0.05), tolerance = tol_dic)
  expect_equivalent(diet_pred_FE$`97.5%`, c(0.18, 0.18), tolerance = tol_dic)
})

diet_pred_RE <- as.data.frame(pred_RE)

test_that("RE predicted probabilities", {
  expect_equivalent(diet_pred_RE$mean, c(0.06, 0.06), tolerance = tol_dic)
  expect_equivalent(diet_pred_RE$sd, c(0.04, 0.04), tolerance = tol_dic)
  expect_equivalent(diet_pred_RE$`2.5%`, c(0.01, 0.01), tolerance = tol_dic)
  expect_equivalent(diet_pred_RE$`50%`, c(0.05, 0.05), tolerance = tol_dic)
  expect_equivalent(diet_pred_RE$`97.5%`, c(0.18, 0.18), tolerance = tol_dic)
})

# Predictions specifying study for baseline
test_that("Specifying study for baseline gives correct result", {
  pred_FE_DART <- predict(diet_fit_FE, type = "response", baseline = "DART")
  expect_identical(c(as.array(pred_FE_DART)),
                   c(as.array(pred_FE_studies)[ , , 1:2]))
})

# Test identical model treating data as IPD
diet_net_ipd <- set_ipd(dietary_fat, 
                        study = studyc,
                        trt = trtc,
                        r = r, 
                        E = E,
                        trt_ref = "Control")

diet_fit_FE_ipd <- nma(diet_net_ipd, 
                       trt_effects = "fixed",
                       prior_intercept = normal(scale = 100),
                       prior_trt = normal(scale = 100))

diet_fit_RE_ipd <- nowarn_on_ci(
                     nma(diet_net_ipd, 
                         trt_effects = "random",
                         prior_intercept = normal(scale = 100),
                         prior_trt = normal(scale = 100),
                         prior_het = half_normal(scale = 5))
                   )

# Relative effects
diet_FE_ipd_releff <- as.data.frame(relative_effects(diet_fit_FE_ipd))

test_that("IPD FE relative effects", {
  expect_equivalent(diet_FE_ipd_releff$mean, -0.01, tolerance = tol)
  expect_equivalent(diet_FE_ipd_releff$sd, 0.054, tolerance = tol)
  expect_equivalent(diet_FE_ipd_releff$`2.5%`, -0.11, tolerance = tol)
  expect_equivalent(diet_FE_ipd_releff$`50%`, -0.01, tolerance = tol)
  expect_equivalent(diet_FE_ipd_releff$`97.5%`, 0.10, tolerance = tol)
})

diet_RE_ipd_releff <- as.data.frame(relative_effects(diet_fit_RE_ipd))

test_that("IPD RE relative effects", {
  expect_equivalent(diet_RE_ipd_releff$mean, -0.02, tolerance = tol)
  expect_equivalent(diet_RE_ipd_releff$sd, 0.09, tolerance = tol)
  expect_equivalent(diet_RE_ipd_releff$`2.5%`, -0.19, tolerance = tol)
  expect_equivalent(diet_RE_ipd_releff$`50%`, -0.01, tolerance = tol)
  expect_equivalent(diet_RE_ipd_releff$`97.5%`, 0.16, tolerance = tol)
})

# RE heterogeneity SD
diet_RE_ipd_sd <- as.data.frame(summary(diet_fit_RE_ipd, pars = "tau"))

test_that("IPD RE heterogeneity SD", {
  expect_equivalent(diet_RE_ipd_sd$mean, 0.13, tolerance = tol)
  expect_equivalent(diet_RE_ipd_sd$sd, 0.12, tolerance = tol)
  expect_equivalent(diet_RE_ipd_sd$`2.5%`, 0.00, tolerance = tol)
  expect_equivalent(diet_RE_ipd_sd$`50%`, 0.10, tolerance = tol)
  expect_equivalent(diet_RE_ipd_sd$`97.5%`, 0.43, tolerance = tol)
})

# DIC
dic_FE_ipd <- dic(diet_fit_FE_ipd)
test_that("IPD FE DIC", {
  expect_equivalent(dic_FE_ipd$resdev, 23.32, tolerance = tol_dic)
  expect_equivalent(dic_FE_ipd$pd, 10.9, tolerance = tol_dic)
  expect_equivalent(dic_FE_ipd$dic, 33.2, tolerance = tol_dic)
})

dic_RE_ipd <- dic(diet_fit_RE_ipd)
test_that("IPD RE DIC", {
  expect_equivalent(dic_RE_ipd$resdev, 21.5, tolerance = tol_dic)
  expect_equivalent(dic_RE_ipd$pd, 13.3, tolerance = tol_dic)
  expect_equivalent(dic_RE_ipd$dic, 34.8, tolerance = tol_dic)
})
```
