---
title: "Example: White blood cell transfusion"
output: rmarkdown::html_vignette
link-citations: yes
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---

```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```
```{r, include=FALSE}
set.seed(2684319)
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

This vignette describes the analysis of 6 trials comparing transfusion of granulocytes (white blood cells) to control for preventing mortality in patients with neutropenia or neutrophil dysfunction [@Stanworth2005; @Turner2012].
The data are available in this package as `transfusion`:
```{r}
head(transfusion)
```

@Turner2012 previously used this dataset to demonstrate the application of informative priors for heterogeneity, an analysis which we recreate here.

## Setting up the network
We begin by setting up the network - here just a pairwise meta-analysis.
We have arm-level count data giving the number of deaths (`r`) out of the total (`n`) in each arm, so we use the function `set_agd_arm()`.
We set "Control" as the reference treatment.
```{r}
tr_net <- set_agd_arm(transfusion, 
                           study = studyc,
                           trt = trtc,
                           r = r, 
                           n = n,
                           trt_ref = "Control")
tr_net
```


## Meta-analysis models
We fit two random effects models, first with a non-informative prior for the heterogeneity, then using the informative prior described by @Turner2012.

### Random effects meta-analysis with non-informative heterogeneity prior
We fit a random effects model using the `nma()` function with `trt_effects = "random"`.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and a non-informative $\textrm{half-N}(5^2)$ prior for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
summary(half_normal(scale = 5))
```

Fitting the RE model
```{r, eval=FALSE, echo=TRUE}
tr_fit_RE_noninf <- nma(tr_net, 
                        trt_effects = "random",
                        prior_intercept = normal(scale = 100),
                        prior_trt = normal(scale = 100),
                        prior_het = half_normal(scale = 5))
```
```{r, echo=FALSE, eval=!params$run_tests}
tr_fit_RE_noninf <- nma(tr_net, 
                        seed = 857369814,
                        trt_effects = "random",
                        prior_intercept = normal(scale = 100),
                        prior_trt = normal(scale = 100),
                        prior_het = half_normal(scale = 5))
```
```{r, echo=FALSE, eval=params$run_tests}
tr_fit_RE_noninf <- suppressWarnings(nma(tr_net, 
                        seed = 857369814,
                        trt_effects = "random",
                        prior_intercept = normal(scale = 100),
                        prior_trt = normal(scale = 100),
                        prior_het = half_normal(scale = 5),
                        iter = 10000,
                        save_warmup = FALSE))
```

Basic parameter summaries are given by the `print()` method:
```{r}
tr_fit_RE_noninf
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(tr_fit_RE_noninf, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r tr_RE_noninf_pp_plot}
plot_prior_posterior(tr_fit_RE_noninf, prior = "het")
```

The posterior distribution for the heterogeneity variance $\tau^2$ is summarised by
```{r}
noninf_tau <- as.array(tr_fit_RE_noninf, pars = "tau")
noninf_tausq <- noninf_tau^2
names(noninf_tausq) <- "tausq"
summary(noninf_tausq)
```


### Random effects meta-analysis with informative heterogeneity prior
Keeping the rest of the model setup the same, we now use an informative $\textrm{log-N}(-3.93, 1.51^2)$ prior for the heterogeneity variance $\tau^2$.
We can examine the range of parameter values implied by this prior distribution with the `summary()` method:
```{r}
summary(log_normal(-3.93, 1.51))
```

Fitting the RE model, we specify the `log_normal` prior distribution in the `prior_het` argument, and set `prior_het_type = "var"` to indicate that this prior distribution is on the variance scale (instead of the standard deviation, the default).
```{r, echo=TRUE, eval=FALSE}
tr_fit_RE_inf <- nma(tr_net, 
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = log_normal(-3.93, 1.51),
                     prior_het_type = "var")
```
```{r, echo=FALSE, eval=!params$run_tests}
tr_fit_RE_inf <- nma(tr_net, 
                     seed = 1803772660,
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = log_normal(-3.93, 1.51),
                     prior_het_type = "var")
```
```{r, echo=FALSE, eval=params$run_tests}
tr_fit_RE_inf <- suppressWarnings(nma(tr_net, 
                     seed = 1803772660,
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = log_normal(-3.93, 1.51),
                     prior_het_type = "var",
                     iter = 10000, save_warmup = FALSE))
```

Basic parameter summaries are given by the `print()` method:
```{r}
tr_fit_RE_inf
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(tr_fit_RE_inf, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r tr_RE_inf_pp_plot}
plot_prior_posterior(tr_fit_RE_inf, prior = "het")
```

> **Note:** The heterogeneity _variance_ $\tau^2$ is plotted here since the prior was specified on $\tau^2$.

The posterior distribution for the heterogeneity variance $\tau^2$ is summarised by
```{r}
inf_tau <- as.array(tr_fit_RE_inf, pars = "tau")
inf_tausq <- inf_tau^2
names(inf_tausq) <- "tausq"
summary(inf_tausq)
```

## References

```{r transfusion_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 2 results ---
library(testthat)

tol <- 0.05

# Non-informative prior
tr_RE_noninf_var <- as.data.frame(summary(noninf_tausq))

test_that("Non-informative RE heterogeneity variance", {
  skip("Non-informative priors not identical")
  expect_equivalent(tr_RE_noninf_var$`50%`, 2.74, tolerance = tol)
  expect_equivalent(tr_RE_noninf_var$`2.5%`, 0.34, tolerance = tol)
  expect_equivalent(tr_RE_noninf_var$`97.5%`, 18.1, tolerance = tol)
})

# Informative prior
tr_RE_inf_var <- as.data.frame(summary(inf_tausq))

test_that("Informative RE heterogeneity variance", {
  expect_equivalent(tr_RE_inf_var$`50%`, 0.18, tolerance = tol)
  expect_equivalent(tr_RE_inf_var$`2.5%`, 0.003, tolerance = tol)
  skip_on_ci()
  expect_equivalent(tr_RE_inf_var$`97.5%`, 1.84, tolerance = tol)
})
```
