---
title: "Example: Diabetes"
output: rmarkdown::html_vignette
link-citations: yes
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---

```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

This vignette describes the analysis of data on the number of new cases of diabetes in 22 trials of 6 antihypertensive drugs [@Elliott2007; @TSD2].
The data are available in this package as `diabetes`:
```{r}
head(diabetes)
```


## Setting up the network
We begin by setting up the network.
We have arm-level count data giving the number of new cases of diabetes (`r`) out of the total (`n`) in each arm, so we use the function `set_agd_arm()`.
For computational efficiency, we let "Beta Blocker" be set as the network reference treatment by default.
@Elliott2007 and @TSD2 use "Diuretic" as the reference, but it is a simple matter to transform the results after fitting the NMA model.^[The gain in efficiency here from using "Beta Blocker" as the network reference treatment instead of "Diuretic" is considerable - around 4-8 times, in terms of effective samples per second.
The functions in this package will always attempt to choose a default network reference treatment that maximises computational efficiency and stability.
If you have chosen an alternative network reference treatment and the model runs very slowly or has low effective sample size, this is a likely cause.]
```{r}
db_net <- set_agd_arm(diabetes, 
                      study = studyc,
                      trt = trtc,
                      r = r, 
                      n = n)
db_net
```

We also have details of length of follow-up in years in each trial (`time`), which we will use as an offset with a cloglog link function to model the data as rates.
We do not have to specify this in the function `set_agd_arm()`: any additional columns in the data (e.g. offsets or covariates, here the column `time`) will automatically be made available in the network.

Plot the network structure.
```{r, eval=FALSE}
plot(db_net, weight_edges = TRUE, weight_nodes = TRUE)
```
```{r diabetes_network_plot, echo=FALSE}
plot(db_net, weight_edges = TRUE, weight_nodes = TRUE) + ggplot2::theme(legend.box.margin = ggplot2::unit(c(0, 0, 0, 4), "lines"))
```

## Meta-analysis models
We fit both fixed effect (FE) and random effects (RE) models.

### Fixed effect meta-analysis
First, we fit a fixed effect model using the `nma()` function with `trt_effects = "fixed"`.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
```

The model is fitted using the `nma()` function.
We specify that a cloglog link will be used with `link = "cloglog"` (the Binomial likelihood is the default for these data), and specify the log follow-up time offset using the regression formula `regression = ~offset(log(time))`.
```{r}
db_fit_FE <- nma(db_net, 
                 trt_effects = "fixed",
                 link = "cloglog",
                 regression = ~offset(log(time)),
                 prior_intercept = normal(scale = 100),
                 prior_trt = normal(scale = 100))
```

Basic parameter summaries are given by the `print()` method:
```{r}
db_fit_FE
```

By default, summaries of the study-specific intercepts $\mu_j$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(db_fit_FE, pars = c("d", "mu"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r db_FE_pp_plot, fig.width=8, fig.height=6, out.width="100%"}
plot_prior_posterior(db_fit_FE)
```

### Random effects meta-analysis
We now fit a random effects model using the `nma()` function with `trt_effects = "random"`.
Again, we use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and we additionally use a $\textrm{half-N}(5^2)$ prior for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
summary(half_normal(scale = 5))
```

Fitting the RE model
```{r}
db_fit_RE <- nma(db_net, 
                 trt_effects = "random",
                 link = "cloglog",
                 regression = ~offset(log(time)),
                 prior_intercept = normal(scale = 10),
                 prior_trt = normal(scale = 10),
                 prior_het = half_normal(scale = 5),
                 init_r = 0.5)
```

Basic parameter summaries are given by the `print()` method:
```{r}
db_fit_RE
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(db_fit_RE, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r db_RE_pp_plot}
plot_prior_posterior(db_fit_RE, prior = c("trt", "het"))
```


### Model comparison
Model fit can be checked using the `dic()` function:
```{r}
(dic_FE <- dic(db_fit_FE))
```
```{r}
(dic_RE <- dic(db_fit_RE))
```

The FE model is a very poor fit to the data, with a residual deviance much higher than the number of data points.
The RE model fits the data better, and has a much lower DIC; we prefer the RE model.

We can also examine the residual deviance contributions with the corresponding `plot()` method.
```{r db_FE_resdev_plot}
plot(dic_FE)
```

```{r db_RE_resdev_plot}
plot(dic_RE)
```


## Further results
For comparison with @Elliott2007 and @TSD2, we can produce relative effects against "Diuretic" using the `relative_effects()` function with `trt_ref = "Diuretic"`:
```{r diabetes_releff_FE, fig.height=3}
(db_releff_FE <- relative_effects(db_fit_FE, trt_ref = "Diuretic"))
plot(db_releff_FE, ref_line = 0)
```
```{r diabetes_releff_RE, fig.height=3}
(db_releff_RE <- relative_effects(db_fit_RE, trt_ref = "Diuretic"))
plot(db_releff_RE, ref_line = 0)
```


@TSD2 produce absolute predictions of the probability of developing diabetes after three years, assuming a Normal distribution on the baseline cloglog probability of developing diabetes on diuretic treatment with mean $-4.2$ and precision $1.11$.
We can replicate these results using the `predict()` method.
We specify a data frame of `newdata`, containing the `time` offset(s) at which to produce predictions (here only 3 years).
The `baseline` argument takes a `distr()` distribution object with which we specify the corresponding Normal distribution on the baseline cloglog probability, and we set `baseline_trt = "Diuretic"` to indicate that the baseline distribution corresponds to "Diuretic" rather than the network reference "Beta Blocker".
We set `type = "response"` to produce predicted event probabilities (`type = "link"` would produce predicted cloglog probabilities).
```{r db_pred_FE, fig.height = 2}
db_pred_FE <- predict(db_fit_FE, 
                      newdata = data.frame(time = 3),
                      baseline = distr(qnorm, mean = -4.2, sd = 1.11^-0.5), 
                      baseline_trt = "Diuretic",
                      type = "response")
db_pred_FE
plot(db_pred_FE)
```
```{r db_pred_RE, fig.height = 2}
db_pred_RE <- predict(db_fit_RE, 
                      newdata = data.frame(time = 3),
                      baseline = distr(qnorm, mean = -4.2, sd = 1.11^-0.5), 
                      baseline_trt = "Diuretic",
                      type = "response")
db_pred_RE
plot(db_pred_RE)
```

If the `baseline` and `newdata` arguments are omitted, predicted probabilities will be produced for every study in the network based on their follow-up times and estimated baseline cloglog probabilities $\mu_j$:
```{r db_pred_RE_all, fig.height=16}
db_pred_RE_studies <- predict(db_fit_RE, type = "response")
db_pred_RE_studies
plot(db_pred_RE_studies)
```

We can also produce treatment rankings, rank probabilities, and cumulative rank probabilities.
```{r diabetes_ranks}
(db_ranks <- posterior_ranks(db_fit_RE))
plot(db_ranks)
```
```{r diabetes_rankprobs}
(db_rankprobs <- posterior_rank_probs(db_fit_RE))
plot(db_rankprobs)
```
```{r diabetes_cumrankprobs}
(db_cumrankprobs <- posterior_rank_probs(db_fit_RE, cumulative = TRUE))
plot(db_cumrankprobs)
```

## References

```{r diabetes_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 2 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# TSD treatment codes
# trt_codes <- c(1 = "Diuretic",
#                2 = "Placebo",
#                3 = "Beta Blocker",
#                4 = "CCB",
#                5 = "ACE Inhibitor",
#                6 = "ARB")

# FE Relative effects
tsd_FE <- tribble(
~trt           , ~mean, ~sd , ~median, ~lower, ~upper,
"Placebo"      , -0.25, 0.06, -0.25  , -0.36 , -0.14 ,
"Beta Blocker" , -0.06, 0.06, -0.06  , -0.17 ,  0.05 ,
"CCB"          , -0.25, 0.05, -0.25  , -0.36 , -0.15 ,
"ACE Inhibitor", -0.36, 0.05, -0.36  , -0.46 , -0.25 ,
"ARB"          , -0.45, 0.06, -0.45  , -0.58 , -0.33 ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_releff_FE <- as.data.frame(db_releff_FE)

test_that("FE relative effects", {
  expect_equivalent(db_releff_FE$mean, tsd_FE$mean, tolerance = tol)
  expect_equivalent(db_releff_FE$sd, tsd_FE$sd, tolerance = tol)
  expect_equivalent(db_releff_FE$`50%`, tsd_FE$median, tolerance = tol)
  expect_equivalent(db_releff_FE$`2.5%`, tsd_FE$lower, tolerance = tol)
  expect_equivalent(db_releff_FE$`97.5%`, tsd_FE$upper, tolerance = tol)
})

# RE Relative effects
tsd_RE <- tribble(
~trt           , ~mean, ~sd , ~median, ~lower, ~upper,
"Placebo"      , -0.29, 0.09, -0.29  , -0.47 , -0.12 ,
"Beta Blocker" , -0.07, 0.09, -0.07  , -0.25 ,  0.10 ,
"CCB"          , -0.24, 0.08, -0.24  , -0.41 , -0.08 ,
"ACE Inhibitor", -0.40, 0.09, -0.40  , -0.58 , -0.24 ,
"ARB"          , -0.47, 0.11, -0.47  , -0.70 , -0.27 ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_releff_RE <- as.data.frame(db_releff_RE)

test_that("RE relative effects", {
  expect_equivalent(db_releff_RE$mean, tsd_RE$mean, tolerance = tol)
  expect_equivalent(db_releff_RE$sd, tsd_RE$sd, tolerance = tol)
  expect_equivalent(db_releff_RE$`50%`, tsd_RE$median, tolerance = tol)
  expect_equivalent(db_releff_RE$`2.5%`, tsd_RE$lower, tolerance = tol)
  expect_equivalent(db_releff_RE$`97.5%`, tsd_RE$upper, tolerance = tol)
})

# Heterogeneity SD
db_tau <- as.data.frame(summary(db_fit_RE, pars = "tau"))

test_that("RE heterogeneity SD", {
  expect_equivalent(db_tau$mean, 0.13, tolerance = tol)
  expect_equivalent(db_tau$sd, 0.04, tolerance = tol)
  expect_equivalent(db_tau$`50%`, 0.12, tolerance = tol)
  expect_equivalent(db_tau$`2.5%`, 0.05, tolerance = tol)
  expect_equivalent(db_tau$`97.5%`, 0.23, tolerance = tol)
})

# FE probabilities
tsd_pred_FE <- tribble(
~trt           , ~mean, ~sd  , ~median, ~lower, ~upper,
"Diuretic"     , 0.065, 0.067, 0.044  , 0.01  ,0.25   ,
"Placebo"      , 0.052, 0.055, 0.034  , 0.01  ,0.20   ,
"Beta Blocker" , 0.062, 0.064, 0.042  , 0.01  ,0.24   ,
"CCB"          , 0.051, 0.055, 0.034  , 0.01  ,0.20   ,
"ACE Inhibitor", 0.047, 0.050, 0.031  , 0.00  ,0.18   ,
"ARB"          , 0.043, 0.046, 0.028  , 0.00  ,0.17   ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_pred_FE <- as.data.frame(db_pred_FE)

test_that("FE predicted probabilities at 3 years", {
  expect_equivalent(db_pred_FE$mean, tsd_pred_FE$mean, tolerance = tol)
  expect_equivalent(db_pred_FE$sd, tsd_pred_FE$sd, tolerance = tol)
  expect_equivalent(db_pred_FE$`50%`, tsd_pred_FE$median, tolerance = tol)
  expect_equivalent(db_pred_FE$`2.5%`, tsd_pred_FE$lower, tolerance = tol)
  expect_equivalent(db_pred_FE$`97.5%`, tsd_pred_FE$upper, tolerance = tol)
})

# RE probabilities
tsd_pred_RE <- tribble(
~trt           , ~mean, ~sd  , ~median, ~lower, ~upper,
"Diuretic"     , 0.065, 0.067, 0.044  , 0.01  ,0.25   ,
"Placebo"      , 0.050, 0.053, 0.033  , 0.01  ,0.20   ,
"Beta Blocker" , 0.061, 0.064, 0.041  , 0.01  ,0.24   ,
"CCB"          , 0.052, 0.056, 0.035  , 0.01  ,0.20   ,
"ACE Inhibitor", 0.045, 0.048, 0.030  , 0.00  ,0.18   ,
"ARB"          , 0.042, 0.046, 0.028  , 0.00  ,0.17   ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_pred_RE <- as.data.frame(db_pred_RE)

test_that("RE predicted probabilities at 3 years", {
  expect_equivalent(db_pred_RE$mean, tsd_pred_RE$mean, tolerance = tol)
  expect_equivalent(db_pred_RE$sd, tsd_pred_RE$sd, tolerance = tol)
  expect_equivalent(db_pred_RE$`50%`, tsd_pred_RE$median, tolerance = tol)
  expect_equivalent(db_pred_RE$`2.5%`, tsd_pred_RE$lower, tolerance = tol)
  expect_equivalent(db_pred_RE$`97.5%`, tsd_pred_RE$upper, tolerance = tol)
})

# RE DIC
test_that("RE DIC", {
  expect_equivalent(dic_RE$resdev, 53.7, tolerance = tol_dic)
  expect_equivalent(dic_RE$pd, 38.0, tolerance = tol_dic)
  expect_equivalent(dic_RE$dic, 91.7, tolerance = tol_dic)
})

# FE DIC
test_that("FE DIC", {
  expect_equivalent(dic_FE$resdev, 78.25, tolerance = tol_dic)
  expect_equivalent(dic_FE$pd, 27.0, tolerance = tol_dic)
  expect_equivalent(dic_FE$dic, 105.2, tolerance = tol_dic)
})

# Check that predictions for multiple studies works in any order
times <- 1:3
# Baselines named by time
bls <- list("1" = distr(qnorm, mean = -4.2, sd = 1.11^-0.5),
            "2" = distr(qnorm, mean = -4.2, sd = 1.11^-0.5),
            "3" = distr(qnorm, mean = -4.2, sd = 1.11^-0.5))

db_pred_FE_multi1 <- as.data.frame(predict(db_fit_FE, 
                      newdata = data.frame(time = times),
                      baseline = unname(bls), 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response"))

db_pred_RE_multi1 <- as.data.frame(predict(db_fit_RE, 
                      newdata = data.frame(time = times),
                      baseline = unname(bls), 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response"))

db_pred_FE_multi2 <- as.data.frame(predict(db_fit_FE, 
                      newdata = data.frame(time = times),
                      baseline = bls, 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response"))

db_pred_RE_multi2 <- as.data.frame(predict(db_fit_RE, 
                      newdata = data.frame(time = times),
                      baseline = bls, 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response"))

db_pred_FE_multi3 <- as.data.frame(predict(db_fit_FE, 
                      newdata = data.frame(time = rev(times)),
                      baseline = bls, 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response")) %>% 
  arrange(.study)

db_pred_RE_multi3 <- as.data.frame(predict(db_fit_RE, 
                      newdata = data.frame(time = rev(times)),
                      baseline = bls, 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response")) %>% 
  arrange(.study)

db_pred_FE_multi4 <- as.data.frame(predict(db_fit_FE, 
                      newdata = data.frame(time = times),
                      baseline = rev(bls), 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response"))

db_pred_RE_multi4 <- as.data.frame(predict(db_fit_RE, 
                      newdata = data.frame(time = times),
                      baseline = rev(bls), 
                      study = time,
                      baseline_trt = "Diuretic",
                      type = "response"))

test_that("Predictions for reordered newdata/baselines works", {
  expect_equivalent(db_pred_FE_multi1$mean,    db_pred_FE_multi2$mean, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$sd,      db_pred_FE_multi2$sd, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`50%`,   db_pred_FE_multi2$`50%`, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`2.5%`,  db_pred_FE_multi2$`2.5%`, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`97.5%`, db_pred_FE_multi2$`97.5%`, tolerance = tol)
  
  expect_equivalent(db_pred_FE_multi1$mean,    db_pred_FE_multi3$mean, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$sd,      db_pred_FE_multi3$sd, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`50%`,   db_pred_FE_multi3$`50%`, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`2.5%`,  db_pred_FE_multi3$`2.5%`, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`97.5%`, db_pred_FE_multi3$`97.5%`, tolerance = tol)
  
  expect_equivalent(db_pred_FE_multi1$mean,    db_pred_FE_multi4$mean, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$sd,      db_pred_FE_multi4$sd, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`50%`,   db_pred_FE_multi4$`50%`, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`2.5%`,  db_pred_FE_multi4$`2.5%`, tolerance = tol)
  expect_equivalent(db_pred_FE_multi1$`97.5%`, db_pred_FE_multi4$`97.5%`, tolerance = tol)
  
  expect_equivalent(db_pred_RE_multi1$mean,    db_pred_RE_multi2$mean, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$sd,      db_pred_RE_multi2$sd, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`50%`,   db_pred_RE_multi2$`50%`, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`2.5%`,  db_pred_RE_multi2$`2.5%`, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`97.5%`, db_pred_RE_multi2$`97.5%`, tolerance = tol)
  
  expect_equivalent(db_pred_RE_multi1$mean,    db_pred_RE_multi3$mean, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$sd,      db_pred_RE_multi3$sd, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`50%`,   db_pred_RE_multi3$`50%`, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`2.5%`,  db_pred_RE_multi3$`2.5%`, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`97.5%`, db_pred_RE_multi3$`97.5%`, tolerance = tol)
  
  expect_equivalent(db_pred_RE_multi1$mean,    db_pred_RE_multi4$mean, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$sd,      db_pred_RE_multi4$sd, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`50%`,   db_pred_RE_multi4$`50%`, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`2.5%`,  db_pred_RE_multi4$`2.5%`, tolerance = tol)
  expect_equivalent(db_pred_RE_multi1$`97.5%`, db_pred_RE_multi4$`97.5%`, tolerance = tol)
})
```
