---
title: "Example: Smoking Cessation"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{Example: Smoking Cessation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8, 
  fig.height = 6
)
```

```{r setup}
library(multinma)
options(mc.cores = parallel::detectCores())
```

This vignette describes the analysis of smoking cessation data [@Hasselblad1998], replicating the analysis in NICE Technical Support Document 4 [@TSD4].
The data are available in this package as `smoking`:
```{r}
head(smoking)
```


### Setting up the network
We begin by setting up the network.
We have arm-level count data giving the number quitting smoking (`r`) out of the total (`n`) in each arm, so we use the function `set_agd_arm()`.
Treatment "No intervention" is set as the network reference treatment.
```{r}
smknet <- set_agd_arm(smoking, 
                      study = studyn,
                      trt = trtc,
                      r = r, 
                      n = n,
                      trt_ref = "No intervention")
smknet
```

Plot the network structure.
```{r smoking_network_plot, eval=2, echo=1}
plot(smknet, weight_edges = TRUE, weight_nodes = TRUE)
plot(smknet, weight_edges = TRUE, weight_nodes = TRUE) + ggplot2::theme(plot.margin = ggplot2::unit(c(1, 1, 1, 6), "lines"))
```

### Random effects NMA
Following TSD 4, we fit a random effects NMA model, using the `nma()` function with `trt_effects = "random"`.
We use $\mathrm{N}(0, 10^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and a $\mathrm{half-N}(5^2)$ prior distribution for the between-study heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 10))
```
```{r}
summary(half_normal(scale = 5))
```

The model is fitted using the `nma()` function.
By default, this will use a Binomial likelihood and a logit link function, auto-detected from the data.
```{r}
smkfit <- nma(smknet, 
              trt_effects = "random",
              prior_intercept = normal(scale = 10),
              prior_trt = normal(scale = 10),
              prior_het = normal(scale = 5))
```

Basic paramter summaries are given by the `print()` method:
```{r}
smkfit
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(smkfit, pars = c("d", "tau", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r smoking_pp_plot}
plot_prior_posterior(smkfit)
```

By default, this displays all model parameters given prior distributions (in this case $d_k$, $\mu_j$, and $\tau$), but this may be changed using the `prior` argument:
```{r smoking_pp_plot_tau}
plot_prior_posterior(smkfit, prior = "het")
```

Model fit can be checked using the `dic()` function
```{r}
(dic_consistency <- dic(smkfit))
```

and the residual deviance contributions examined with the corresponding `plot()` method
```{r smoking_resdev_plot}
plot(dic_consistency)
```

Overall model fit seems to be adequate, with almost all points showing good fit (mean residual deviance contribution of 1).
The only two points with higher residual deviance (i.e. worse fit) correspond to the two zero counts in the data:
```{r}
smoking[smoking$r == 0, ]
```


### Checking for inconsistency
We fit an unrelated mean effects (UME) model [@TSD4] to assess the consistency assumption.
Again, we use the function `nma()`, but now with the argument `consistency = "ume"`.
```{r}
smkfit_ume <- nma(smknet, 
                  consistency = "ume",
                  trt_effects = "random",
                  prior_intercept = normal(scale = 10),
                  prior_trt = normal(scale = 10),
                  prior_het = normal(scale = 5))
smkfit_ume
```

Comparing the model fit statistics
```{r}
dic_consistency
(dic_ume <- dic(smkfit_ume))
```

We see that there is little to choose between the two models.
However, it is also important to examine the individual contributions to model fit of each data point under the two models (a so-called "dev-dev" plot).
Passing two `nma_dic` objects produced by the `dic()` function to the `plot()` method produces this dev-dev plot:
```{r smoking_devdev_plot}
plot(dic_consistency, dic_ume, point_alpha = 0.5, interval_alpha = 0.2)
```

All points lie roughly on the line of equality, so there is no evidence for inconsistency here.

### Further results
Pairwise relative effects, for all pairwise contrasts with `all_contrasts = TRUE`.
```{r smoking_releff}
(smk_releff <- relative_effects(smkfit, all_contrasts = TRUE))
plot(smk_releff, ref_line = 0)
```

Treatment rankings, rank probabilities, and cumulative rank probabilities.
We set `lower_better = FALSE` since a higher log odds of cessation is better (the outcome is positive).
```{r smoking_ranks, fig.height=3}
(smk_ranks <- posterior_ranks(smkfit, lower_better = FALSE))
plot(smk_ranks)
```
```{r smoking_rankprobs}
(smk_rankprobs <- posterior_rank_probs(smkfit, lower_better = FALSE))
plot(smk_rankprobs)
```
```{r smoking_cumrankprobs}
(smk_cumrankprobs <- posterior_rank_probs(smkfit, lower_better = FALSE, cumulative = TRUE))
plot(smk_cumrankprobs)
```

## References

```{r smoking_tests, eval=FALSE, include=FALSE}
#--- Test against TSD 4 results ---
library(testthat)
library(dplyr)

# A = No intervention
# B = Self-help
# C = Individual counselling
# D = Group counselling

trt_codes <- c(A = "No intervention",
               B = "Self-help",
               C = "Individual counselling",
               D = "Group counselling")

# Relative effects
tsd_re <- tribble(
  ~contrast, ~est, ~sd, ~lower, ~upper,
  "dAB", 0.49, 0.40, -0.29, 1.31,
  "dAC", 0.84, 0.24,  0.39, 1.34,
  "dAD", 1.10, 0.44,  0.26, 2.00,
  "dBC", 0.35, 0.41, -0.46, 1.18,
  "dBD", 0.61, 0.49, -0.34, 1.59,
  "dCD", 0.26, 0.41, -0.55, 1.09) %>% 
  mutate(trt_b = recode(substr(contrast, 2, 2),
                        !!! trt_codes),
         trt = recode(substr(contrast, 3, 3),
                        !!! trt_codes),
         trt_b = ordered(trt_b, levels = levels(smknet$treatments)),
         trt = ordered(trt, levels = levels(smknet$treatments)),
         rev = if_else(trt_b > trt, -1, 1),
         .l = lower, .u = upper,
         lower = if_else(trt_b > trt, .u, .l),
         upper = if_else(trt_b > trt, .l, .u)) %>% 
  arrange(trt_b, trt) %>% 
  mutate_at(vars(est, lower, upper), ~.*rev)

expect_equal(smk_releff$summary$mean, tsd_re$est, tol = 0.01)
expect_equal(smk_releff$summary$sd, tsd_re$sd, tol = 0.01)
expect_equal(smk_releff$summary$`2.5%`, tsd_re$lower, tol = 0.05)
expect_equal(smk_releff$summary$`97.5%`, tsd_re$upper, tol = 0.05)

# Heterogeneity SD
smk_tau <- summary(smkfit, pars = "tau")
expect_equal(smk_tau$summary$`50%`, 0.82, tol = 0.01)
expect_equal(smk_tau$summary$sd, 0.19, tol = 0.01)
expect_equal(smk_tau$summary$`2.5%`, 0.55, tol = 0.05)
expect_equal(smk_tau$summary$`97.5%`, 1.27, tol = 0.05)

# DIC
expect_equal(dic_consistency$resdev, 54.0, tol = 0.1)
expect_equal(dic_consistency$pd, 45.0, tol = 0.1)
expect_equal(dic_consistency$dic, 99.0, tol = 0.1)

# Relative effects (UME)
tsd_ume <- tribble(
  ~contrast, ~est, ~sd, ~lower, ~upper,
  "dAB",  0.34, 0.58, -0.81, 1.50,
  "dAC",  0.86, 0.27,  0.34, 1.43,
  "dAD",  1.43, 0.88, -0.21, 3.29,
  "dBC", -0.05, 0.74, -1.53, 1.42,
  "dBD",  0.65, 0.73, -0.80, 2.12,
  "dCD",  0.20, 0.78, -1.37, 1.73)  %>% 
  mutate(trt_b = recode(substr(contrast, 2, 2),
                        !!! trt_codes),
         trt = recode(substr(contrast, 3, 3),
                        !!! trt_codes),
         trt_b = ordered(trt_b, levels = levels(smknet$treatments)),
         trt = ordered(trt, levels = levels(smknet$treatments)),
         rev = if_else(trt_b > trt, -1, 1),
         .l = lower, .u = upper,
         lower = if_else(trt_b > trt, .u, .l),
         upper = if_else(trt_b > trt, .l, .u)) %>% 
  arrange(trt_b, trt) %>% 
  mutate_at(vars(est:upper), ~.*rev)

smk_ume_releff <- summary(smkfit_ume, pars = "d")

expect_equal(smk_ume_releff$summary$mean, tsd_ume$est, tol = 0.01)
expect_equal(smk_ume_releff$summary$sd, tsd_ume$sd, tol = 0.01)
expect_equal(smk_ume_releff$summary$`2.5%`, tsd_ume$lower, tol = 0.05)
expect_equal(smk_ume_releff$summary$`97.5%`, tsd_ume$upper, tol = 0.05)

# Heterogeneity SD (UME)
smk_ume_tau <- summary(smkfit_ume, pars = "tau")
expect_equal(smk_ume_tau$summary$`50%`, 0.89, tol = 0.01)
expect_equal(smk_ume_tau$summary$sd, 0.22, tol = 0.01)
expect_equal(smk_ume_tau$summary$`2.5%`, 0.58, tol = 0.05)
expect_equal(smk_ume_tau$summary$`97.5%`, 1.45, tol = 0.05)

# DIC (UME)
expect_equal(dic_ume$resdev, 53.4, tol = 0.1)
expect_equal(dic_ume$pd, 46.1, tol = 0.1)
expect_equal(dic_ume$dic, 99.5, tol = 0.1)
```

