---
title: "Example: Smoking cessation"
output: rmarkdown::html_vignette
link-citations: yes
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---

```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

This vignette describes the analysis of smoking cessation data [@Hasselblad1998], replicating the analysis in NICE Technical Support Document 4 [@TSD4].
The data are available in this package as `smoking`:
```{r}
head(smoking)
```


## Setting up the network
We begin by setting up the network.
We have arm-level count data giving the number quitting smoking (`r`) out of the total (`n`) in each arm, so we use the function `set_agd_arm()`.
Treatment "No intervention" is set as the network reference treatment.
```{r}
smknet <- set_agd_arm(smoking, 
                      study = studyn,
                      trt = trtc,
                      r = r, 
                      n = n,
                      trt_ref = "No intervention")
smknet
```

Plot the network structure.
```{r, eval=FALSE}
plot(smknet, weight_edges = TRUE, weight_nodes = TRUE)
```
```{r smoking_network_plot, echo=FALSE, fig.width=8, fig.height=6, out.width="100%"}
plot(smknet, weight_edges = TRUE, weight_nodes = TRUE) + ggplot2::theme(plot.margin = ggplot2::unit(c(1, 1, 1, 6), "lines"))
```

## Random effects NMA
Following TSD 4, we fit a random effects NMA model, using the `nma()` function with `trt_effects = "random"`.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and a $\textrm{half-N}(5^2)$ prior distribution for the between-study heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
```
```{r}
summary(half_normal(scale = 5))
```

The model is fitted using the `nma()` function.
By default, this will use a Binomial likelihood and a logit link function, auto-detected from the data.
```{r}
smkfit <- nma(smknet, 
              trt_effects = "random",
              prior_intercept = normal(scale = 100),
              prior_trt = normal(scale = 100),
              prior_het = normal(scale = 5))
```

Basic parameter summaries are given by the `print()` method:
```{r}
smkfit
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(smkfit, pars = c("d", "tau", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r smoking_pp_plot, fig.width=8, fig.height=6, out.width="100%"}
plot_prior_posterior(smkfit)
```

By default, this displays all model parameters given prior distributions (in this case $d_k$, $\mu_j$, and $\tau$), but this may be changed using the `prior` argument:
```{r smoking_pp_plot_tau}
plot_prior_posterior(smkfit, prior = "het")
```

Model fit can be checked using the `dic()` function
```{r}
(dic_consistency <- dic(smkfit))
```

and the residual deviance contributions examined with the corresponding `plot()` method
```{r smoking_resdev_plot, fig.width=8}
plot(dic_consistency)
```

Overall model fit seems to be adequate, with almost all points showing good fit (mean residual deviance contribution of 1).
The only two points with higher residual deviance (i.e. worse fit) correspond to the two zero counts in the data:
```{r}
smoking[smoking$r == 0, ]
```


## Checking for inconsistency

> **Note:** The results of the inconsistency models here are slightly different to those of Dias et al. [-@Dias2010; -@TSD4], although the overall conclusions are the same.
> This is due to the presence of multi-arm trials and a different ordering of treatments, meaning that inconsistency is parameterised differently within the multi-arm trials.
> The same results as Dias et al. are obtained if the network is instead set up with `trtn` as the treatment variable.

### Unrelated mean effects
We first fit an unrelated mean effects (UME) model [@TSD4] to assess the consistency assumption.
Again, we use the function `nma()`, but now with the argument `consistency = "ume"`.
```{r}
smkfit_ume <- nma(smknet, 
                  consistency = "ume",
                  trt_effects = "random",
                  prior_intercept = normal(scale = 100),
                  prior_trt = normal(scale = 100),
                  prior_het = normal(scale = 5))
smkfit_ume
```

Comparing the model fit statistics
```{r}
dic_consistency
(dic_ume <- dic(smkfit_ume))
```

We see that there is little to choose between the two models.
However, it is also important to examine the individual contributions to model fit of each data point under the two models (a so-called "dev-dev" plot).
Passing two `nma_dic` objects produced by the `dic()` function to the `plot()` method produces this dev-dev plot:
```{r smoking_devdev_plot}
plot(dic_consistency, dic_ume, point_alpha = 0.5, interval_alpha = 0.2)
```

All points lie roughly on the line of equality, so there is no evidence for inconsistency here.

### Node-splitting
Another method for assessing inconsistency is node-splitting [@TSD4; @Dias2010].
Whereas the UME model assesses inconsistency globally, node-splitting assesses inconsistency locally for each potentially inconsistent comparison (those with both direct and indirect evidence) in turn.

Node-splitting can be performed using the `nma()` function with the argument `consistency = "nodesplit"`.
By default, all possible comparisons will be split (as determined by the `get_nodesplits()` function).
Alternatively, a specific comparison or comparisons to split can be provided to the `nodesplit` argument.
```{r}
smk_nodesplit <- nma(smknet, 
                     consistency = "nodesplit",
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = normal(scale = 5))
```

The `summary()` method summarises the node-splitting results, displaying the direct and indirect estimates $d_\mathrm{dir}$ and $d_\mathrm{ind}$ from each node-split model, the network estimate $d_\mathrm{net}$ from the consistency model, the inconsistency factor $\omega = d_\mathrm{dir} - d_\mathrm{ind}$, and a Bayesian $p$-value for inconsistency on each comparison.
Since random effects models are fitted, the heterogeneity standard deviation $\tau$ under each node-split model and under the consistency model is also displayed.
The DIC model fit statistics are also provided.
```{r}
summary(smk_nodesplit)
```

The DIC of each inconsistency model is unchanged from the consistency model, no node-splits result in reduced heterogeneity standard deviation $\tau$ compared to the consistency model, and the Bayesian $p$-values are all large.
There is no evidence of inconsistency.

We can visually compare the posterior distributions of the direct, indirect, and network estimates using the `plot()` method.
These are all in agreement; the posterior densities of the direct and indirect estimates overlap.
Notice that there is not much indirect information for the Individual counselling vs. No intervention comparison, so the network (consistency) estimate is very similar to the direct estimate for this comparison.
```{r smk_nodesplit, fig.width = 7}
plot(smk_nodesplit) +
  ggplot2::theme(legend.position = "bottom", legend.direction = "horizontal")
```

## Further results
Pairwise relative effects, for all pairwise contrasts with `all_contrasts = TRUE`.
```{r smoking_releff, fig.height=4.5}
(smk_releff <- relative_effects(smkfit, all_contrasts = TRUE))
plot(smk_releff, ref_line = 0)
```

Treatment rankings, rank probabilities, and cumulative rank probabilities.
We set `lower_better = FALSE` since a higher log odds of cessation is better (the outcome is positive).
```{r smoking_ranks, fig.height=3}
(smk_ranks <- posterior_ranks(smkfit, lower_better = FALSE))
plot(smk_ranks)
```
```{r smoking_rankprobs}
(smk_rankprobs <- posterior_rank_probs(smkfit, lower_better = FALSE))
plot(smk_rankprobs)
```
```{r smoking_cumrankprobs}
(smk_cumrankprobs <- posterior_rank_probs(smkfit, lower_better = FALSE, cumulative = TRUE))
plot(smk_cumrankprobs)
```

## References

```{r smoking_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 4 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# A = No intervention
# B = Self-help
# C = Individual counselling
# D = Group counselling

trt_codes <- c(A = "No intervention",
               B = "Self-help",
               C = "Individual counselling",
               D = "Group counselling")

# Relative effects
tsd_re <- tribble(
  ~contrast, ~est, ~sd, ~lower, ~upper,
  "dAB", 0.49, 0.40, -0.29, 1.31,
  "dAC", 0.84, 0.24,  0.39, 1.34,
  "dAD", 1.10, 0.44,  0.26, 2.00,
  "dBC", 0.35, 0.41, -0.46, 1.18,
  "dBD", 0.61, 0.49, -0.34, 1.59,
  "dCD", 0.26, 0.41, -0.55, 1.09) %>% 
  mutate(trt_b = recode(substr(contrast, 2, 2),
                        !!! trt_codes),
         trt = recode(substr(contrast, 3, 3),
                        !!! trt_codes),
         trt_b = ordered(trt_b, levels = levels(smknet$treatments)),
         trt = ordered(trt, levels = levels(smknet$treatments)),
         rev = if_else(trt_b > trt, -1, 1),
         .l = lower, .u = upper,
         lower = if_else(trt_b > trt, .u, .l),
         upper = if_else(trt_b > trt, .l, .u)) %>% 
  arrange(trt_b, trt) %>% 
  mutate_at(vars(est, lower, upper), ~.*rev)

test_that("RE relative effects", {
  expect_equivalent(smk_releff$summary$mean, tsd_re$est, tolerance = tol)
  expect_equivalent(smk_releff$summary$sd, tsd_re$sd, tolerance = tol)
  expect_equivalent(smk_releff$summary$`2.5%`, tsd_re$lower, tolerance = tol)
  expect_equivalent(smk_releff$summary$`97.5%`, tsd_re$upper, tolerance = tol)
})

# Heterogeneity SD
smk_tau <- summary(smkfit, pars = "tau")

test_that("RE heterogeneity SD", {
  expect_equivalent(smk_tau$summary$`50%`, 0.82, tolerance = tol)
  expect_equivalent(smk_tau$summary$sd, 0.19, tolerance = tol)
  expect_equivalent(smk_tau$summary$`2.5%`, 0.55, tolerance = tol)
  expect_equivalent(smk_tau$summary$`97.5%`, 1.27, tolerance = tol)
})

# DIC
test_that("DIC", {
  expect_equivalent(dic_consistency$resdev, 54.0, tolerance = tol_dic)
  expect_equivalent(dic_consistency$pd, 45.0, tolerance = tol_dic)
  expect_equivalent(dic_consistency$dic, 99.0, tolerance = tol_dic)
})

# Relative effects (UME)

# Treatment ordering is different in TSD 4 - use trtn instead which reflects this
smknet2 <- set_agd_arm(smoking, studyn, trtn, r = r, n = n, trt_ref = 1)
smkfit_ume2 <- nma(smknet2, 
                   consistency = "ume",
                   trt_effects = "random",
                   prior_intercept = normal(scale = 100),
                   prior_trt = normal(scale = 100),
                   prior_het = normal(scale = 5),
                   iter = 4000)

# Results of modified TSD 4 model including multi-arm correction
tsd_ume <- tribble(
  ~contrast, ~est, ~sd, ~lower, ~upper,
  # "dAB",  0.34, 0.58, -0.81, 1.50,
  # "dAC",  0.86, 0.27,  0.34, 1.43,
  # "dAD",  1.43, 0.88, -0.21, 3.29,
  # "dBC", -0.05, 0.74, -1.53, 1.42,
  # "dBD",  0.65, 0.73, -0.80, 2.12,
  # "dCD",  0.20, 0.78, -1.37, 1.73)  %>% 
  "dAB",  0.34, 0.59, -0.82, 1.51,
  "dAC",  0.90, 0.28,  0.37, 1.49,
  "dAD",  1.12, 0.80, -0.36, 2.80,
  "dBC",  0.04, 0.73, -1.39, 1.50,
  "dBD",  0.61, 0.72, -0.80, 2.05,
  "dCD",  0.20, 0.79, -1.40, 1.75)
  # mutate(trt_b = recode(substr(contrast, 2, 2),
  #                       !!! trt_codes),
  #        trt = recode(substr(contrast, 3, 3),
  #                       !!! trt_codes),
  #        trt_b = ordered(trt_b, levels = levels(smknet$treatments)),
  #        trt = ordered(trt, levels = levels(smknet$treatments)),
  #        rev = if_else(trt_b > trt, -1, 1),
  #        .l = lower, .u = upper,
  #        lower = if_else(trt_b > trt, .u, .l),
  #        upper = if_else(trt_b > trt, .l, .u)) %>% 
  # arrange(trt_b, trt) %>% 
  # mutate_at(vars(est:upper), ~.*rev)

smk_ume_releff <- summary(smkfit_ume2, pars = "d")

test_that("UME relative effects", {
  # skip("Different model parameterisation")
  expect_equivalent(smk_ume_releff$summary$mean, tsd_ume$est, tolerance = tol)
  expect_equivalent(smk_ume_releff$summary$sd, tsd_ume$sd, tolerance = tol)
  expect_equivalent(smk_ume_releff$summary$`2.5%`, tsd_ume$lower, tolerance = tol)
  expect_equivalent(smk_ume_releff$summary$`97.5%`, tsd_ume$upper, tolerance = tol)
})

# Heterogeneity SD (UME)
smk_ume_tau <- summary(smkfit_ume2, pars = "tau")

test_that("UME heterogeneity SD", {
  # skip("Different model parameterisation")
  # expect_equivalent(smk_ume_tau$summary$`50%`, 0.89, tolerance = tol)
  # expect_equivalent(smk_ume_tau$summary$sd, 0.22, tolerance = tol)
  # expect_equivalent(smk_ume_tau$summary$`2.5%`, 0.58, tolerance = tol)
  # expect_equivalent(smk_ume_tau$summary$`97.5%`, 1.45, tolerance = tol)
  expect_equivalent(smk_ume_tau$summary$`50%`, 0.91, tolerance = tol)
  expect_equivalent(smk_ume_tau$summary$sd, 0.21, tolerance = tol)
  expect_equivalent(smk_ume_tau$summary$`2.5%`, 0.59, tolerance = tol)
  expect_equivalent(smk_ume_tau$summary$`97.5%`, 1.48, tolerance = tol)
})

# DIC (UME)
test_that("UME DIC", {
  expect_equivalent(dic_ume$resdev, 53.4, tolerance = tol_dic)
  expect_equivalent(dic_ume$pd, 46.1, tolerance = tol_dic)
  expect_equivalent(dic_ume$dic, 99.5, tolerance = tol_dic)
})

dic_ume2 <- dic(smkfit_ume2)
test_that("UME DIC", {
  expect_equivalent(dic_ume2$resdev, 53.4, tolerance = tol_dic)
  expect_equivalent(dic_ume2$pd, 46.1, tolerance = tol_dic)
  expect_equivalent(dic_ume2$dic, 99.5, tolerance = tol_dic)
})

# Check that multinomial ordered model produces same results
smknet3 <- set_agd_arm(smoking,
                       studyn,
                       trtc,
                       r = multi(nonevent = n, event = r, inclusive = TRUE),
                       trt_ref = "No intervention")
smkfit_ord <- nma(smknet3,
              trt_effects = "random",
              link = "logit",
              prior_intercept = normal(scale = 100),
              prior_trt = normal(scale = 100),
              prior_het = normal(scale = 5),
              prior_aux = flat())


smk_ord_releff <- relative_effects(smkfit_ord, all_contrasts = TRUE)
test_that("Equivalent ordered multinomial RE relative effects", {
  expect_equivalent(smk_ord_releff$summary$mean, tsd_re$est, tolerance = tol)
  expect_equivalent(smk_ord_releff$summary$sd, tsd_re$sd, tolerance = tol)
  expect_equivalent(smk_ord_releff$summary$`2.5%`, tsd_re$lower, tolerance = tol)
  expect_equivalent(smk_ord_releff$summary$`97.5%`, tsd_re$upper, tolerance = tol)
})

smk_ord_tau <- summary(smkfit_ord, pars = "tau")
test_that("Equivalent ordered multinomial RE heterogeneity SD", {
  expect_equivalent(smk_ord_tau$summary$`50%`, 0.82, tolerance = tol)
  expect_equivalent(smk_ord_tau$summary$sd, 0.19, tolerance = tol)
  expect_equivalent(smk_ord_tau$summary$`2.5%`, 0.55, tolerance = tol)
  expect_equivalent(smk_ord_tau$summary$`97.5%`, 1.27, tolerance = tol)
})

# DIC
dic_ord <- dic(smkfit_ord)
test_that("Equivalent ordered multinomial DIC", {
  expect_equivalent(dic_ord$resdev, 54.0, tolerance = tol_dic)
  expect_equivalent(dic_ord$pd, 45.0, tolerance = tol_dic)
  expect_equivalent(dic_ord$dic, 99.0, tolerance = tol_dic)
})

test_that("Robust to custom options(contrasts) settings", {
  skip_on_cran()
  
  withr::with_options(list(contrasts = c(ordered = "contr.SAS",
                                                       unordered = "contr.SAS")), {
    smkfit_SAS <- nma(smknet,
                      trt_effects = "random",
                      prior_intercept = normal(scale = 100),
                      prior_trt = normal(scale = 100),
                      prior_het = normal(scale = 5))
    
    smkfit_SAS_summary <- as_tibble(summary(smkfit_SAS))[, c("parameter", "mean", "sd")]
    smkfit_SAS_releff <- as_tibble(relative_effects(smkfit_SAS))[, c("parameter", "mean", "sd")]
    smkfit_SAS_pred <- as_tibble(predict(smkfit_SAS))[, c("parameter", "mean", "sd")]
    
    smkfit_ume_SAS <- nma(smknet,
                      trt_effects = "random",
                      consistency = "ume",
                      prior_intercept = normal(scale = 100),
                      prior_trt = normal(scale = 100),
                      prior_het = normal(scale = 5))
    
    smkfit_ume_SAS_summary <- as_tibble(summary(smkfit_ume_SAS))[, c("parameter", "mean", "sd")]
  })

  expect_equal(smkfit_SAS_summary,
               as_tibble(summary(smkfit))[, c("parameter", "mean", "sd")],
               tolerance = tol)
  expect_equal(smkfit_SAS_releff,
               as_tibble(relative_effects(smkfit))[, c("parameter", "mean", "sd")],
               tolerance = tol)
  expect_equal(smkfit_SAS_pred,
               as_tibble(predict(smkfit))[, c("parameter", "mean", "sd")],
               tolerance = tol)
  
  expect_equal(smkfit_ume_SAS_summary,
               as_tibble(summary(smkfit_ume))[, c("parameter", "mean", "sd")],
               tolerance = tol)
})
```

