---
title: "Example: Plaque psoriasis ML-NMR"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---

```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```

```{r setup}
library(multinma)
library(dplyr)      # dplyr and tidyr for data manipulation
library(tidyr)
library(ggplot2)    # ggplot2 for plotting covariate distributions
```
```{r, eval = FALSE}
options(mc.cores = parallel::detectCores())
```
```{r, echo = FALSE}
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

Simulated individual patient data (IPD) from trials comparing treatments for plaque psoriasis are found in the data set `plaque_psoriasis_ipd`.
Aggregate data (AgD) are available on a further set of trials, found in the data set `plaque_psoriasis_agd`.
In this vignette, we recreate the multilevel network meta-regression (ML-NMR) analyses performed by @methods_paper [see also @Phillippo_thesis].
We will analyse IPD from three studies, UNCOVER-1, UNCOVER-2, and UNCOVER-3 [@Griffiths2015;@Gordon2016], and AgD from one study, FIXTURE [@Langley2014].

```{r}
pso_ipd <- filter(plaque_psoriasis_ipd,
                  studyc %in% c("UNCOVER-1", "UNCOVER-2", "UNCOVER-3"))

pso_agd <- filter(plaque_psoriasis_agd,
                  studyc == "FIXTURE")

head(pso_ipd)
head(pso_agd)
```

We consider running a ML-NMR adjusting for five potential effect-modifying covariates: duration of psoriasis `durnpso`, weight `weight`, previous systemic treatment `prevsys`, body surface area `bsa`, and psoriatic arthritis `psa`.

# Setup
## Preparing the data
We need to prepare the data so that it is in an acceptable format to run a ML-NMR model.
Firstly, we need to handle the binary covariates `prevsys` and `psa`.
In the IPD, these are coded as `TRUE` or `FALSE`, but in the AgD these are coded as percentages (out of 100).
We need these to transform both of these sets of variables so that they are numeric and lie in the interval $[0,1]$, so that the variables are compatible across the data sources.
Whilst we are here, we also transform body surface area `bsa` (a percentage) to lie in $[0,1]$, since that will make specifying an appropriate marginal distribution easier later, and rescale `weight` and `duration` to aid interpretation of the regression coefficients (in terms of 10 kilos and 10 years respectively).
We also add in a `trtclass` variable, indicating which treatments belong to which classes.
Finally, we check for missing values in the IPD.
```{r}
pso_ipd <- pso_ipd %>% 
  mutate(# Variable transformations
         bsa = bsa / 100,
         prevsys = as.numeric(prevsys),
         psa = as.numeric(psa),
         weight = weight / 10,
         durnpso = durnpso / 10,
         # Treatment classes
         trtclass = case_when(trtn == 1 ~ "Placebo",
                              trtn %in% c(2, 3, 5, 6) ~ "IL blocker",
                              trtn == 4 ~ "TNFa blocker"),
         # Check complete cases for covariates of interest
         complete = complete.cases(durnpso, prevsys, bsa, weight, psa)
  )

pso_agd <- pso_agd %>% 
  mutate(
    # Variable transformations
    bsa_mean = bsa_mean / 100,
    bsa_sd = bsa_sd / 100,
    prevsys = prevsys / 100,
    psa = psa / 100,
    weight_mean = weight_mean / 10,
    weight_sd = weight_sd / 10,
    durnpso_mean = durnpso_mean / 10,
    durnpso_sd = durnpso_sd / 10,
    # Treatment classes
    trtclass = case_when(trtn == 1 ~ "Placebo",
                              trtn %in% c(2, 3, 5, 6) ~ "IL blocker",
                              trtn == 4 ~ "TNFa blocker")
  )
```

A small number of individuals have missing covariates:
```{r}
sum(!pso_ipd$complete)
mean(!pso_ipd$complete)
```

Since the proportion of missing data is so small, we will simply exclude these individuals from the analysis.
```{r}
pso_ipd <- filter(pso_ipd, complete)
```

## Creating the network
Set up the network, setting the IPD with `set_ipd()`, AgD (arm-based) with `set_agd_arm()`, and combining together using `combine_network()`.
We specify the binary `pasi75` outcome as `r` in the IPD, and the count outcome `pasi75_r` and denominator `pasi75_n` as `r` and `n` in the AgD.
We specify the treatment classes with `trt_class = trtclass`.
```{r}
pso_net <- combine_network(
  set_ipd(pso_ipd, 
          study = studyc, 
          trt = trtc, 
          r = pasi75,
          trt_class = trtclass),
  set_agd_arm(pso_agd, 
              study = studyc, 
              trt = trtc, 
              r = pasi75_r, 
              n = pasi75_n,
              trt_class = trtclass)
)

pso_net
```

We can produce a network plot with the `plot()` method:
```{r pso_network_plot, fig.width=8, fig.height=6, out.width="100%"}
plot(pso_net, weight_nodes = TRUE, weight_edges = TRUE, show_trt_class = TRUE) + 
  ggplot2::theme(legend.position = "bottom", legend.box = "vertical")
```

## Numerical integration for ML-NMR
ML-NMR models define the meta-regression model at the individual level, in exactly the same manner as a full-IPD meta-regression.
ML-NMR then incorporates the AgD into the model by integrating this individual-level model over the covariate distribution in each AgD study [@methods_paper;@Phillippo_thesis].
Using integration, instead of simply "plugging-in" mean covariate values for the AgD studies, avoids aggregation bias when the link function is not the identity function.

This package utilises numerical integration to incorporate the aggregate data - specifically, quasi-Monte Carlo (QMC) integration with a Gaussian copula [@methods_paper;@Phillippo_thesis].
QMC integration is a very general and flexible integration approach, which typically requires far fewer integration points than standard (pseudo-random) Monte-Carlo integration to achieve the same numerical accuracy.^[The convergence rate of QMC is typically $\mathcal{O}(1/n)$, whereas the expected convergence rate of standard MC is $\mathcal{O}(1/n^\frac{1}{2})$ [@Caflisch1998;@Niederreiter1978].]
A Gaussian copula allows us to account for correlations between covariates, which may have any specified marginal distributions.

We now set up the numerical integration for the network.
The five covariates that we will consider adjusting for are body surface area `bsa`, duration of psoriasis `durnpso`, previous systemic treatment `prevsys`, psoriatic arthritis `psa`, and weight `weight`.
We need to choose suitable marginal distributions for these covariates to draw the integration points from.
`prevsys` and `psa` are binary covariates, so these are given a Bernoulli distribution.
`bsa` is a percentage, so we choose a logit-Normal distribution.
We choose Gamma distributions for `durnpso` and `weight` to account for skewness.
These choices seem to match well the marginal distributions observed in the IPD:
```{r pso_covariate_plot}
# Get mean and sd of covariates in each study
ipd_summary <- pso_ipd %>% 
  group_by(studyc) %>% 
  summarise_at(vars(weight, durnpso, bsa), list(mean = mean, sd = sd, min = min, max = max)) %>% 
  pivot_longer(weight_mean:bsa_max, names_sep = "_", names_to = c("covariate", ".value")) %>% 
  # Assign distributions
  mutate(dist = recode(covariate,
                       bsa = "dlogitnorm",
                       durnpso = "dgamma",
                       weight = "dgamma")) %>% 
  # Compute density curves
  group_by(studyc, covariate) %>% 
  mutate(value = if_else(dist == "dlogitnorm",
                         list(seq(0, 1, length.out = 101)),
                         list(seq(min*0.8, max*1.2, length.out = 101)))) %>% 
  unnest(cols = value) %>% 
  mutate(dens = do.call(first(dist), args = list(x = value, mean = first(mean), sd = first(sd))))

# Plot histograms and assumed densities
pso_ipd %>% 
  pivot_longer(c(weight, durnpso, bsa), names_to = "covariate", values_to = "value") %>% 
ggplot(aes(x = value)) +
  geom_histogram(aes(y = stat(density)), 
                 binwidth = function(x) diff(range(x)) / nclass.Sturges(x),
                 boundary = 0,
                 fill = "grey50") +
  geom_line(aes(y = dens), data = ipd_summary,
            colour = "darkred", size = 0.5) +
  facet_wrap(~studyc + covariate, scales = "free", ncol = 3) +
  theme_multinma()
```

We add integration points to the AgD studies in the network using the `add_integration()` function.
Marginal distributions for each covariate are specified using the `distr()` function, which takes a cumulative distribution function corresponding to the chosen marginal distribution, and arguments to that distribution as column names in the aggregate data.
(Note: This package provides several convenience functions for specifying these distributions, including `qgamma()` which allows for a parameterisation of the Gamma distribution in terms of mean and standard deviation, `qbern()` which provides the Bernoulli distribution, and `qlogitnorm()` which provides the logit-Normal distribution allowing for a parameterisation in terms of mean and standard deviation.)
Since we do not know the correlations between covariates in the AgD studies, we impute these with the weighted mean of the correlations in the IPD studies (the default option).
```{r}
pso_net <- add_integration(pso_net,
  durnpso = distr(qgamma, mean = durnpso_mean, sd = durnpso_sd),
  prevsys = distr(qbern, prob = prevsys),
  bsa = distr(qlogitnorm, mean = bsa_mean, sd = bsa_sd),
  weight = distr(qgamma, mean = weight_mean, sd = weight_sd),
  psa = distr(qbern, prob = psa),
  n_int = 1000
)
```

# ML-NMR models
We fit both fixed effect (FE) and random effects (RE) ML-NMR models.

## Fixed effect ML-NMR
First, we fit a FE ML-NMR model using the function `nma()`.
Following [@methods_paper] we specify weakly-informative $N(0, 10^2)$ priors on each parameter.
The range of parameter values implied by these prior distributions can be checked using the `summary()` method:
```{r}
summary(normal(scale = 10))
```

The regression model is specified with `regression = ~(durnpso + prevsys + bsa + weight + psa)*.trt`, which will include the main (prognostic) effects of each covariate as well as interactions with treatment.
We use a probit link function (`link = "probit"`), and specify that the two-parameter Binomial approximation for the aggregate-level likelihood should be used (`likelihood = "bernoulli2"`, where "bernoulli" refers to the individual-level likelihood, and "2" denotes the two-parameter adjustment to the aggregate-level likelihood) [@methods_paper].
We utilise the shared effect modifier assumption to help identify the model, setting treatment-covariate interactions to be equal within each class (`class_interactions = "common"`).
We narrow the possible range for random initial values with `init_r = 0.1` (the default is `init_r = 2`), since probit models in particular are often hard to initialise.
Using the QR decomposition (`QR = TRUE`) greatly improves sampling efficiency here, as is often the case for regression models.
```{r}
pso_fit_FE <- nma(pso_net, 
                  trt_effects = "fixed",
                  link = "probit", 
                  likelihood = "bernoulli2",
                  regression = ~(durnpso + prevsys + bsa + weight + psa)*.trt,
                  class_interactions = "common",
                  prior_intercept = normal(scale = 10),
                  prior_trt = normal(scale = 10),
                  prior_reg = normal(scale = 10),
                  init_r = 0.1,
                  QR = TRUE)
```

Basic parameter summaries are given by the `print()` method:
```{r}
print(pso_fit_FE)
```

By default, summaries of the study-specific intercepts $\mu_j$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(pso_fit_FE, pars = c("d", "beta", "mu"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r pso_FE_pp_plot, fig.width=8, fig.height=6, out.width="100%"}
plot_prior_posterior(pso_fit_FE, prior = c("intercept", "trt", "reg"))
```

Plots of estimated numerical integration error are produced using the `plot_integration_error()` function:
```{r pso_FE_cumint}
plot_integration_error(pso_fit_FE)
```

## Random effects ML-NMR
We now fit a RE model.
Again, we specify weakly-informative $N(0, 10^2)$ priors on each parameter, and now specify a $\textrm{half-N}(0, 2.5^2)$ prior for the heterogeneity standard deviation $\tau$.
The range of parameter values implied by these prior distributions can be checked using the `summary()` method:
```{r}
summary(normal(scale = 10))
summary(half_normal(scale = 2.5))
```

Fitting the model uses the same call to `nma()` as before, except now with `trt_effects = "random"`.
```{r, eval=!params$run_tests}
pso_fit_RE <- nma(pso_net, 
                  trt_effects = "random",
                  link = "probit", 
                  likelihood = "bernoulli2",
                  regression = ~(durnpso + prevsys + bsa + weight + psa)*.trt,
                  class_interactions = "common",
                  prior_intercept = normal(scale = 10),
                  prior_trt = normal(scale = 10),
                  prior_reg = normal(scale = 10),
                  prior_het = half_normal(scale = 2.5),
                  init_r = 0.1,
                  QR = TRUE)
```

Basic parameter summaries are given by the `print()` method:
```{r, eval=!params$run_tests}
print(pso_fit_RE)
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(pso_fit_RE, pars = c("d", "beta", "tau", "mu", "delta"))
```

There are a number of divergent transitions, which we can investigate using the `pairs()` method:
```{r pso_RE_pairs, eval=!params$run_tests}
pairs(pso_fit_RE, pars = c("delta[UNCOVER-2: ETN]", "d[ETN]", "tau", "lp__"))
```

The divergent transition errors (red crosses) seem to be concentrated in the upper tail of the heterogeneity standard deviation parameter.
This suggests that the information to identify the heterogeneity parameter is weak - we have only four studies in the network - and that a more informative prior distribution might aid estimation.

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r pso_RE_pp_plot, eval=!params$run_tests, fig.width=8, fig.height=6, out.width="100%"}
plot_prior_posterior(pso_fit_RE, prior = c("intercept", "trt", "reg", "het"))
```

Plots of estimated numerical integration error are produced using the `plot_integration_error()` function:
```{r pso_RE_cumint, eval=!params$run_tests}
plot_integration_error(pso_fit_RE)
```

# Model comparison
The model fit under the FE and RE models can be checked using the `dic()` function.
```{r, eval=!params$run_tests}
(pso_dic_FE <- dic(pso_fit_FE))
(pso_dic_RE <- dic(pso_fit_RE))
```
```{r, eval=params$run_tests, echo=FALSE}
(pso_dic_FE <- dic(pso_fit_FE))
```

The DIC is similar between the FE and RE models, suggesting that there is little evidence for any residual heterogeneity.

# Further results
Parameter estimates can be plotted using the `plot()` method, for example to examine the estimated regression coefficients:
```{r}
plot(pso_fit_FE,
     pars = "beta",
     stat = "halfeye",
     ref_line = 0)
```

We can produce population-adjusted relative effects for each study population in the network using the `relative_effects()` function.
```{r pso_releff_FE}
(pso_releff_FE <- relative_effects(pso_fit_FE))
plot(pso_releff_FE, ref_line = 0)
```

Predicted probabilities of achieving PASI 75 in each study population on each treatment are produced using the `predict()` method.
The argument `type = "reponse"` specifies that we want predicted probabilities, rather than probit probabilities.
```{r pso_pred_FE}
(pso_pred_FE <- predict(pso_fit_FE, type = "response"))
plot(pso_pred_FE, ref_line = c(0, 1))
```

We can produce population-adjusted ranks, rank probabilities, and cumulative rank probabilities in each study population using the `posterior_ranks()` and `posterior_rank_probs()` functions.
We specify `lower_better = FALSE`, since a higher outcome is better (higher chance of achieving PASI 75).
```{r pso_ranks_FE}
(pso_ranks_FE <- posterior_ranks(pso_fit_FE, lower_better = FALSE))
plot(pso_ranks_FE)
```

```{r pso_rankprobs_FE}
(pso_rankprobs_FE <- posterior_rank_probs(pso_fit_FE, lower_better = FALSE))
plot(pso_rankprobs_FE)
```

```{r pso_cumrankprobs_FE}
(pso_cumrankprobs_FE <- posterior_rank_probs(pso_fit_FE, lower_better = FALSE, cumulative = TRUE))
plot(pso_cumrankprobs_FE)
```

All of the above estimates (relative effects, predictions, rankings) can also be produced for a specific target population or populations by providing a suitable `newdata` argument to for function (and a `baseline` distribution for `predict()`).

To produce population-adjusted relative effects (and corresponding rankings) for a chosen target population, we require only the mean covariate values in that population.
For example, `newdata` could provide the following mean covariate values:
```{r}
new_agd_means <- tibble(
  bsa = 0.6,
  prevsys = 0.1,
  psa = 0.2,
  weight = 10,
  durnpso = 3)
```

Population-adjusted relative effects in this target population are then calculated using the `relative_effects()` function, and can be plotted with the corresponding `plot()` method:
```{r pso_releff_FE_new}
(pso_releff_FE_new <- relative_effects(pso_fit_FE, newdata = new_agd_means))
plot(pso_releff_FE_new, ref_line = 0)
```

For absolute predictions, we require information about the full covariate distribution in the target population, not just the mean values.
If IPD are available for the target population, `newdata` is simply a data frame of the IPD.
If AgD are available for the target population, `newdata` must be a data frame with added integration points created using the `add_integration()` function.
 
For example, suppose the aggregate target population introduced above had the following covariate means and standard deviations (for continuous covariates) or proportions (for discrete covariates):
```{r}
new_agd_int <- tibble(
  bsa_mean = 0.6,
  bsa_sd = 0.3,
  prevsys = 0.1,
  psa = 0.2,
  weight_mean = 10,
  weight_sd = 1,
  durnpso_mean = 3,
  durnpso_sd = 1
)
```

We add integration points to this data frame in a similar manner to before.
Again, we need to supply a correlation matrix for the joint covariate distribution; we use the same weighted mean correlation matrix computed earlier from the IPD in the network, which is stored in the network object as `int_cor`.
```{r}
new_agd_int <- add_integration(new_agd_int,
  durnpso = distr(qgamma, mean = durnpso_mean, sd = durnpso_sd),
  prevsys = distr(qbern, prob = prevsys),
  bsa = distr(qlogitnorm, mean = bsa_mean, sd = bsa_sd),
  weight = distr(qgamma, mean = weight_mean, sd = weight_sd),
  psa = distr(qbern, prob = psa),
  cor = pso_net$int_cor,
  n_int = 1000)
```

Predicted probabilities of achieving PASI 75 in this target population, given a $N(-1.75, 0.08^2)$ distribution on the baseline probit-probability of response on Placebo (at the reference levels of the covariates), are then produced using the `predict()` method:
```{r pso_pred_FE_new}
(pso_pred_FE_new <- predict(pso_fit_FE, 
                            type = "response",
                            newdata = new_agd_int,
                            baseline = distr(qnorm, -1.75, 0.08)))
plot(pso_pred_FE_new, ref_line = c(0, 1))
```

# References

```{r pso_tests, include=FALSE, eval=params$run_tests}
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# FE model parameters
test_fe <- tribble(
  ~parameter                            , ~mean, ~sd , ~`2.5%`, ~`50%`, ~`97.5%`,
  "beta[durnpso]"                       , 0.05 , 0.06, -0.08  , 0.05  , 0.17    ,
  "beta[prevsys]"                       , -0.13, 0.16, -0.44  , -0.13 , 0.17    ,
  "beta[bsa]"                           , -0.06, 0.45, -0.98  , -0.05 , 0.78    ,
  "beta[weight]"                        , 0.04 , 0.03, -0.02  , 0.04  , 0.10    ,
  "beta[psa]"                           , -0.08, 0.17, -0.42  , -0.08 , 0.25    ,
  "beta[durnpso:.trtclassTNFa blocker]", -0.03, 0.08, -0.18  , -0.03 , 0.12    ,
  "beta[durnpso:.trtclassIL blocker]"  , -0.01, 0.07, -0.15  , -0.01 , 0.12    ,
  "beta[prevsys:.trtclassTNFa blocker]", 0.19 , 0.19, -0.19  , 0.19  , 0.56    ,
  "beta[prevsys:.trtclassIL blocker]"  , 0.06 , 0.17, -0.28  , 0.06  , 0.40    ,
  "beta[bsa:.trtclassTNFa blocker]"    , 0.05 , 0.52, -0.95  , 0.04  , 1.10    ,
  "beta[bsa:.trtclassIL blocker]"      , 0.29 , 0.49, -0.64  , 0.29  , 1.27    ,
  "beta[weight:.trtclassTNFa blocker]" , -0.17, 0.04, -0.23  , -0.17 , -0.10   ,
  "beta[weight:.trtclassIL blocker]"   , -0.10, 0.03, -0.16  , -0.10 , -0.03   ,
  "beta[psa:.trtclassTNFa blocker]"    , -0.06, 0.21, -0.46  , -0.06 , 0.37    ,
  "beta[psa:.trtclassIL blocker]"      , 0.00 , 0.18, -0.35  , 0.00  , 0.37    ,
  "d[ETN]"                              , 1.55 , 0.08, 1.39   , 1.55  , 1.72    ,
  "d[IXE_Q2W]"                          , 2.95 , 0.09, 2.79   , 2.95  , 3.13    ,
  "d[IXE_Q4W]"                          , 2.54 , 0.08, 2.38   , 2.54  , 2.71    ,
  "d[SEC_150]"                          , 2.14 , 0.11, 1.93   , 2.14  , 2.37    ,
  "d[SEC_300]"                          , 2.45 , 0.12, 2.22   , 2.45  , 2.69    )

summary_fe <- summary(pso_fit_FE, pars = c("beta", "d")) %>% 
  as_tibble() %>% 
  select(parameter, mean, sd, `2.5%`, `50%`, `97.5%`)

test_that("FE model parameters", {
  expect_equal(summary_fe, test_fe, tolerance = tol, check.attributes = FALSE)
})

# FE DIC
test_that("FE DIC", {
  expect_equivalent(pso_dic_FE$resdev, 3129.4, tolerance = tol_dic)
  expect_equivalent(pso_dic_FE$pd, 24.1, tolerance = tol_dic)
  expect_equivalent(pso_dic_FE$dic, 3153.5, tolerance = tol_dic)
})

# Population average relative effects in target population
test_releff_fe_new <- tribble(
  ~parameter         , ~mean, ~sd , ~`2.5%`, ~`50%`, ~`97.5%`,
  "d[New 1: ETN]"    , 1.25 , 0.24, 0.81 , 1.24, 1.73  ,
  "d[New 1: IXE_Q2W]", 2.89 , 0.23, 2.46 , 2.88, 3.36  ,
  "d[New 1: IXE_Q4W]", 2.48 , 0.23, 2.05 , 2.47, 2.94  ,
  "d[New 1: SEC_150]", 2.08 , 0.23, 1.64 , 2.07, 2.55  ,
  "d[New 1: SEC_300]", 2.39 , 0.23, 1.95 , 2.38, 2.86  )

summary_releff_fe_new <- pso_releff_FE_new %>% 
  as_tibble() %>% 
  select(parameter, mean, sd, `2.5%`, `50%`, `97.5%`)

test_that("FE PATE in target population", {
  expect_equal(summary_releff_fe_new, test_releff_fe_new, tolerance = tol, check.attributes = FALSE)
})

# Check construction of all contrasts
pso_releff_FE_all_contr <- relative_effects(pso_fit_FE, all_contrasts = TRUE)

# Reconstruct from basic contrasts in each study
dk <- function(study, trt, sims = pso_releff_FE$sims) {
  if (trt == "PBO") return(0)
  else return(sims[ , , paste0("d[", study, ": ", trt, "]"), drop = FALSE])
}

test_all_contr <- tibble(
  contr = pso_releff_FE_all_contr$summary$parameter,
  study = factor(stringr::str_extract(contr, "(?<=\\[)(.+)(?=:)")),
  trtb = stringr::str_extract(contr, "(?<=\\: )(.+)(?= vs\\.)"),
  trta = stringr::str_extract(contr, "(?<=vs\\. )(.+)(?=\\])")
) %>% 
  rowwise() %>% 
  mutate(as_tibble(multinma:::summary.mcmc_array(dk(study, trtb) - dk(study, trta)))) %>% 
  select(.study = study, parameter = contr, mean:Rhat)

test_that("Construction of all contrasts is correct", {
  expect_equal(pso_releff_FE_all_contr$summary, test_all_contr, check.attributes = FALSE)
})

# Check all contrasts in target population
pso_releff_FE_all_contr_new <- relative_effects(pso_fit_FE, newdata = new_agd_means, all_contrasts = TRUE)

test_all_contr_new <- tibble(
  contr = pso_releff_FE_all_contr_new$summary$parameter,
  study = factor(stringr::str_extract(contr, "(?<=\\[)(.+)(?=:)")),
  trtb = stringr::str_extract(contr, "(?<=\\: )(.+)(?= vs\\.)"),
  trta = stringr::str_extract(contr, "(?<=vs\\. )(.+)(?=\\])")
) %>% 
  rowwise() %>% 
  mutate(as_tibble(multinma:::summary.mcmc_array(dk(study, trtb, pso_releff_FE_new$sims) - dk(study, trta, pso_releff_FE_new$sims)))) %>% 
  select(.study = study, parameter = contr, mean:Rhat)

test_that("Construction of all contrasts in target population is correct", {
  expect_equal(pso_releff_FE_all_contr_new$summary, test_all_contr_new, check.attributes = FALSE)
})

# Population average response probabilities in target population
test_pred_fe_new <- tribble(
  ~parameter            , ~mean, ~sd , ~`2.5%`, ~`50%`, ~`97.5%`,
  "pred[New 1: PBO]"    , 0.06 , 0.03, 0.02   , 0.06  , 0.12    ,
  "pred[New 1: ETN]"    , 0.37 , 0.06, 0.26   , 0.37  , 0.48    ,
  "pred[New 1: IXE_Q2W]", 0.90 , 0.03, 0.84   , 0.90  , 0.94    , 
  "pred[New 1: IXE_Q4W]", 0.81 , 0.04, 0.72   , 0.81  , 0.88    ,
  "pred[New 1: SEC_150]", 0.68 , 0.06, 0.57   , 0.68  , 0.78    ,
  "pred[New 1: SEC_300]", 0.78 , 0.05, 0.68   , 0.78  , 0.86    )

summary_pred_fe_new <- pso_pred_FE_new %>% 
  as_tibble() %>% 
  select(parameter, mean, sd, `2.5%`, `50%`, `97.5%`)

test_that("FE average response probabilities in target population", {
  expect_equal(summary_pred_fe_new, test_pred_fe_new, tolerance = tol, check.attributes = FALSE)
})
```
