---
title: "Example: BCG vaccine for tuberculosis"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
params:
  run_tests: FALSE
---

```{r, code=readLines("children/knitr_setup.R"), include=FALSE}
```
```{r, include=FALSE}
set.seed(18284729)
```

```{r, eval = FALSE}
library(multinma)
options(mc.cores = parallel::detectCores())
```
```{r setup, echo = FALSE}
library(multinma)
nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)
```

This vignette describes the analysis of 13 trials investigating BCG vaccination vs. no vaccination for prevention of Tuberculosis (TB) [@TSD3;@Berkey1995].
The data are available in this package as `bcg_vaccine`:
```{r}
head(bcg_vaccine)
```

@TSD3 used these data to demonstrate meta-regression models adjusting for the continuous covariate `latitude`, the absolute degrees latitude at which the study was conducted, which we recreate here.

### Setting up the network
We have data giving the number diagnosed with TB during trial follow-up (`r`) out of the total (`n`) in each arm, so we use the function `set_agd_arm()` to set up the network.
We set "unvaccinated" as the network reference treatment.
```{r}
bcg_net <- set_agd_arm(bcg_vaccine, 
                       study = studyn,
                       trt = trtc,
                       r = r, 
                       n = n,
                       trt_ref = "Unvaccinated")
bcg_net
```

The `latitude` variable in the `bcg_vaccine` data frame will automatically be available to use in a meta-regression model.

### Meta-analysis models
We fit random effects (RE) models, firstly without any covariates, and then with a meta-regression on the continuous covariate `latitude`.

#### RE meta-analysis (no covariate)
We start by fitting a standard RE model without any covariates.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effect $d_\mathrm{Vaccine}$ and study-specific intercepts $\mu_j$, and a $\textrm{half-N}(0, 5^2)$ prior distribution for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
summary(half_normal(scale = 5))
```

The model is fitted with the `nma()` function, with a random effects model specified by `trt_effects = "random"`.
```{r, eval = FALSE}
bcg_fit_unadj <- nma(bcg_net, 
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = half_normal(scale = 5))
```
```{r, echo = FALSE}
bcg_fit_unadj <- nma(bcg_net, 
                     seed = 14308133,
                     trt_effects = "random",
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_het = half_normal(scale = 5))
```

Basic parameter summaries are given by the `print()` method:
```{r}
bcg_fit_unadj
```

By default, summaries of the study-specific intercepts $\mu_j$ and random effects $\delta_j$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(bcg_fit_unadj, pars = c("d", "mu", "delta", "tau"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r bcg_unadj_pp_plot}
plot_prior_posterior(bcg_fit_unadj, prior = c("trt", "het"))
```

#### RE meta-regression with covariate `latitude`
We now fit a RE meta-regression model, adjusting for `latitude`.
We use $\mathrm{N}(0, 100^2)$ prior distributions for the treatment effect $d_\mathrm{Vaccine}$, study-specific intercepts $\mu_j$, and regression coefficient $\beta$.
We use a $\text{half-N}(0, 5^2)$ prior distribution for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 100))
summary(half_normal(scale = 5))
```

Again, the model is fitted with the `nma()` function.
The `regression` formula `~ .trt:latitude` means that the interaction of latitude with treatment will be included; the `.trt` special variable indicates treatment, and `latitude` is in the original data set.
We increase `adapt_delta` to 0.99 to remove a small number of divergent transition errors (the default for RE models is set to 0.95).
```{r, eval = FALSE}
bcg_fit_lat <- nma(bcg_net, 
                   trt_effects = "random",
                   regression = ~.trt:latitude,
                   prior_intercept = normal(scale = 100),
                   prior_trt = normal(scale = 100),
                   prior_reg = normal(scale = 100),
                   prior_het = half_normal(scale = 5),
                   adapt_delta = 0.99)
```
```{r, echo = FALSE}
bcg_fit_lat <- nowarn_on_ci(
                 nma(bcg_net, 
                     seed = 1932599147,
                     trt_effects = "random",
                     regression = ~.trt:latitude,
                     prior_intercept = normal(scale = 100),
                     prior_trt = normal(scale = 100),
                     prior_reg = normal(scale = 100),
                     prior_het = half_normal(scale = 5),
                     adapt_delta = 0.99)
                 )
```

Basic parameter summaries are given by the `print()` method:
```{r}
bcg_fit_lat
```

Note that `latitude` has automatically been centered at 33.46, the mean value for the studies in the network.

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(bcg_fit_lat, pars = c("d", "beta", "mu", "delta", "tau"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r bcg_lat_pp_plot}
plot_prior_posterior(bcg_fit_lat, prior = c("trt", "reg", "het"))
```

### Model fit and comparison
Model fit can be checked using the `dic()` function:
```{r}
(bcg_dic_unadj <- dic(bcg_fit_unadj))
```
```{r}
(bcg_dic_lat <- dic(bcg_fit_lat))
```

The DIC is very similar between the two models, so we might at first choose the unadjusted model.
The posterior mean residual deviance is larger for the model with the covariate, but this model also has a lower effective number of parameters $p_D$ so is allowing for more shrinkage of the random treatment effects.
Moreover, the model with the covariate has a much lower estimated heterogeneity standard deviation:
```{r}
summary(bcg_fit_unadj, pars = "tau")
summary(bcg_fit_lat, pars = "tau")
```

Adjusting for latitude is explaining a substantial amount of heterogeneity in the data.
The 95% Credible Interval for the regression coefficient also excludes zero:
```{r bcg_vaccine_beta_lat, fig.height = 4}
summary(bcg_fit_lat, pars = "beta")

plot(bcg_fit_lat, 
     pars = "beta", 
     ref_line = 0,
     stat = "halfeye")
```


Altogether, we might prefer the model with the adjustment for latitude.
When considering covariates in random effects models it is important not to just look at the DIC [@TSD3].
We should also consider any reductions in heterogeneity, and the estimated regression coefficients and their standard error.
The DIC is not sensitive to changes in the heterogeneity, as RE models are very flexible and can fit the data well whatever the level of heterogeneity.

## Further results
We can produce estimates of the relative effect of vaccination at any latitude using the `relative_effects()` function.
The `newdata` argument specifies a data frame containing the values of the covariate `latitude` that we are interested in, and the `study` argument is used to specify a column of `newdata` for an informative label.
```{r}
bcg_releff_lat <- relative_effects(bcg_fit_lat,
                                   newdata = tibble::tibble(latitude = seq(10, 50, by = 10),
                                                            label = paste0(latitude, "\u00B0 latitude")),
                                   study = label)

bcg_releff_lat
```

The `plot()` method may be used to visually compare these estimates:
```{r bcg_vaccine_releff_lat, fig.height = 5}
plot(bcg_releff_lat, 
     ref_line = 0)
```

A more sophisticated plot shows the regression line and confidence band for the effect of latitude, overlaid on the observed log odds ratios in each study:
```{r bcg_vaccine_reg_plot}
library(dplyr)
library(ggplot2)

# Get data for regression line
lat_range <- range(bcg_vaccine$latitude)
lat_dat <- tibble(latitude = seq(lat_range[1], lat_range[2], by = 1))

bcg_lat_reg <- relative_effects(bcg_fit_lat, 
                                newdata = lat_dat) %>% 
  as_tibble() %>% 
  bind_cols(lat_dat)

# Get study log odds ratios
bcg_lor <- bcg_vaccine %>% 
  group_by(studyn) %>% 
  mutate(lor = log(r / (n - r)) - log(first(r) / (first(n) - first(r))),
         sample_size = sum(n)) %>% 
  slice(-1)

# Plot
ggplot(aes(x = latitude), data = bcg_lor) +
  geom_hline(yintercept = 0, colour = "grey60") +
  geom_ribbon(aes(ymin = `2.5%`, ymax = `97.5%`), data = bcg_lat_reg,
              fill = "darkred", alpha = 0.3) +
  geom_line(aes(y = mean), data = bcg_lat_reg,
            colour = "darkred") +
  geom_point(aes(y = lor, size = sample_size), alpha = 0.6) +
  coord_cartesian(xlim = c(0, 60)) +
  xlab("Degrees Latitude") + ylab("log Odds Ratio") +
  scale_size("Sample Size") +
  theme_multinma()
```

## References

```{r bcg_vaccine_tests, include=FALSE, eval=params$run_tests}
#--- Test against TSD 3 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# Relative effects
bcg_unadj_releff <- as.data.frame(summary(bcg_fit_unadj, pars = "d"))

test_that("Unadjusted relative effects", {
  expect_equivalent(bcg_unadj_releff$mean, -0.762, tolerance = tol)
  expect_equivalent(bcg_unadj_releff$sd, 0.22, tolerance = tol)
  expect_equivalent(bcg_unadj_releff$`2.5%`, -1.21, tolerance = tol)
  expect_equivalent(bcg_unadj_releff$`97.5%`, -0.34, tolerance = tol)
})

bcg_lat_releff <- as.data.frame(summary(bcg_fit_lat, pars = "d"))

test_that("Regression relative effects", {
  expect_equivalent(bcg_lat_releff$mean, -0.763, tolerance = tol)
  expect_equivalent(bcg_lat_releff$sd, 0.126, tolerance = tol)
  expect_equivalent(bcg_lat_releff$`2.5%`, -1.04, tolerance = tol)
  expect_equivalent(bcg_lat_releff$`97.5%`, -0.52, tolerance = tol)
})

# Regression coefficients
bcg_lat_beta <- as.data.frame(summary(bcg_fit_lat, pars = "beta"))

test_that("Regression beta", {
  expect_equivalent(bcg_lat_beta$mean, -0.032, tolerance = tol)
  expect_equivalent(bcg_lat_beta$sd, 0.009, tolerance = tol)
  expect_equivalent(bcg_lat_beta$`2.5%`, -0.05, tolerance = tol)
  expect_equivalent(bcg_lat_beta$`97.5%`, -0.01, tolerance = tol)
})

# RE heterogeneity SD
bcg_unadj_sd <- as.data.frame(summary(bcg_fit_unadj, pars = "tau"))

test_that("Unadjusted heterogeneity SD", {
  expect_equivalent(bcg_unadj_sd$`50%`, 0.649, tolerance = tol)
  expect_equivalent(bcg_unadj_sd$sd, 0.202, tolerance = tol)
  expect_equivalent(bcg_unadj_sd$`2.5%`, 0.39, tolerance = tol)
  expect_equivalent(bcg_unadj_sd$`97.5%`, 1.17, tolerance = tol)
})

bcg_lat_sd <- as.data.frame(summary(bcg_fit_lat, pars = "tau"))

test_that("Regression heterogeneity SD", {
  expect_equivalent(bcg_lat_sd$`50%`, 0.272, tolerance = tol)
  expect_equivalent(bcg_lat_sd$sd, 0.188, tolerance = tol)
  expect_equivalent(bcg_lat_sd$`2.5%`, 0.03, tolerance = tol)
  expect_equivalent(bcg_lat_sd$`97.5%`, 0.75, tolerance = tol)
})

# DIC
test_that("Unadjusted DIC", {
  expect_equivalent(bcg_dic_unadj$resdev, 26.1, tolerance = tol_dic)
  expect_equivalent(bcg_dic_unadj$pd, 23.5, tolerance = tol_dic)
  expect_equivalent(bcg_dic_unadj$dic, 49.6, tolerance = tol_dic)
})

test_that("Regression DIC", {
  expect_equivalent(bcg_dic_lat$resdev, 30.4, tolerance = tol_dic)
  expect_equivalent(bcg_dic_lat$pd, 21.1, tolerance = tol_dic)
  expect_equivalent(bcg_dic_lat$dic, 51.5, tolerance = tol_dic)
})
```
