---
title: "Example: Diabetes"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{Example: Diabetes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8, 
  fig.height = 6,
  eval = identical(Sys.getenv("NOT_CRAN"), "true")
)
options(width = 100)
```

```{r setup}
library(multinma)
options(mc.cores = parallel::detectCores())
```

This vignette describes the analysis of data on the number of new cases of diabetes in 22 trials of 6 antihypertensive drugs [@Elliott2007; @TSD2].
The data are available in this package as `diabetes`:
```{r}
head(diabetes)
```


### Setting up the network
We begin by setting up the network.
We have arm-level count data giving the number of new cases of diabetes (`r`) out of the total (`n`) in each arm, so we use the function `set_agd_arm()`.
Treatment "Diuretic" is set as the network reference treatment following @Elliott2007.
```{r}
db_net <- set_agd_arm(diabetes, 
                      study = studyc,
                      trt = trtc,
                      r = r, 
                      n = n,
                      trt_ref = "Diuretic")
db_net
```

We also have details of length of follow-up in years in each trial (`time`), which we will use as an offset with a cloglog link function to model the data as rates.
We do not have to specify this in the function `set_agd_arm()`: any additional columns in the data (e.g. offsets or covariates, here the column `time`) will automatically be made available in the network.

Plot the network structure.
```{r, eval=FALSE}
plot(db_net, weight_edges = TRUE, weight_nodes = TRUE)
```
```{r diabetes_network_plot, echo=FALSE}
plot(db_net, weight_edges = TRUE, weight_nodes = TRUE) + ggplot2::theme(legend.box.margin = ggplot2::unit(c(0, 0, 0, 4), "lines"))
```

### Meta-analysis models
We fit both fixed effect (FE) and random effects (RE) models.

#### Fixed effect meta-analysis
First, we fit a fixed effect model using the `nma()` function with `trt_effects = "fixed"`.
We use $\mathrm{N}(0, 10^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 10))
```

The model is fitted using the `nma()` function.
We specify that a cloglog link will be used with `link = "cloglog"` (the Binomial likelihood is the default for these data), and specify the log follow-up time offset using the regression formula `regression = ~offset(log(time))`.
```{r}
db_fit_FE <- nma(db_net, 
                 trt_effects = "fixed",
                 link = "cloglog",
                 regression = ~offset(log(time)),
                 prior_intercept = normal(scale = 10),
                 prior_trt = normal(scale = 10))
```

Basic paramter summaries are given by the `print()` method:
```{r}
db_fit_FE
```

By default, summaries of the study-specific intercepts $\mu_j$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(db_fit_FE, pars = c("d", "mu"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r db_FE_pp_plot}
plot_prior_posterior(db_fit_FE)
```

#### Random effects meta-analysis
We now fit a random effects model using the `nma()` function with `trt_effects = "random"`.
Again, we use $\mathrm{N}(0, 10^2)$ prior distributions for the treatment effects $d_k$ and study-specific intercepts $\mu_j$, and we additionally use a $\mathrm{half-N}(5^2)$ prior for the heterogeneity standard deviation $\tau$.
We can examine the range of parameter values implied by these prior distributions with the `summary()` method:
```{r}
summary(normal(scale = 10))
summary(half_normal(scale = 5))
```

Fitting the RE model
```{r, warning=FALSE}
db_fit_RE <- nma(db_net, 
                 trt_effects = "random",
                 link = "cloglog",
                 regression = ~offset(log(time)),
                 prior_intercept = normal(scale = 10),
                 prior_trt = normal(scale = 10),
                 prior_het = half_normal(scale = 5))
```

Basic paramter summaries are given by the `print()` method:
```{r}
db_fit_RE
```

By default, summaries of the study-specific intercepts $\mu_j$ and study-specific relative effects $\delta_{jk}$ are hidden, but could be examined by changing the `pars` argument:
```{r, eval=FALSE}
# Not run
print(db_fit_FE, pars = c("d", "mu", "delta"))
```

The prior and posterior distributions can be compared visually using the `plot_prior_posterior()` function:
```{r db_RE_pp_plot}
plot_prior_posterior(db_fit_RE, prior = c("trt", "het"))
```


#### Model comparison
Model fit can be checked using the `dic()` function:
```{r}
(dic_FE <- dic(db_fit_FE))
```
```{r}
(dic_RE <- dic(db_fit_RE))
```

The FE model is a very poor fit to the data, with a residual deviance much higher than the number of data points.
The RE model fits the data better, and has a much lower DIC; we prefer the RE model.

We can also examine the residual deviance contributions with the corresponding `plot()` method.
```{r db_FE_resdev_plot}
plot(dic_FE)
```

```{r db_RE_resdev_plot}
plot(dic_RE)
```


### Further results
@TSD2 produce absolute predictions of the probability of developing diabetes after three years, assuming a Normal distribution on the baseline cloglog probability of developing diabetes on diuretic treatment with mean $-4.2$ and precision $1.11$.
We can replicate these results using the `predict()` method.
We specify a data frame of `newdata`, containing the `time` offset(s) at which to produce predictions (here only 3 years).
The `baseline` argument takes a `distr()` distribution object, with which we specify the corresponding Normal distribution on the baseline cloglog probability.
We set `type = "response"` to produce predicted rates (`type = "link"` would produce predicted cloglog probabilities).
```{r db_pred_FE, fig.height = 2}
pred_FE <- predict(db_fit_FE, 
                   newdata = data.frame(time = 3),
                   baseline = distr(qnorm, mean = -4.2, sd = 1.11^-0.5), 
                   type = "response")
pred_FE
plot(pred_FE)
```
```{r db_pred_RE, fig.height = 2}
pred_RE <- predict(db_fit_RE, 
                   newdata = data.frame(time = 3),
                   baseline = distr(qnorm, mean = -4.2, sd = 1.11^-0.5), 
                   type = "response")
pred_RE
plot(pred_RE)
```

If the `baseline` and `newdata` arguments are ommitted, predicted probabilities will be produced for every study in the network based on their follow-up times and estimated baseline cloglog probabilities $\mu_j$:
```{r db_pred_RE_all, fig.height=16}
pred_RE_studies <- predict(db_fit_RE, type = "response")
pred_RE_studies
plot(pred_RE_studies)
```

We can also produce treatment rankings, rank probabilities, and cumulative rank probabilities.
```{r diabetes_ranks}
(db_ranks <- posterior_ranks(db_fit_RE))
plot(db_ranks)
```
```{r diabetes_rankprobs}
(db_rankprobs <- posterior_rank_probs(db_fit_RE))
plot(db_rankprobs)
```
```{r diabetes_cumrankprobs}
(db_cumrankprobs <- posterior_rank_probs(db_fit_RE, cumulative = TRUE))
plot(db_cumrankprobs)
```

## References

```{r diabetes_tests, include=FALSE, error=TRUE}
#--- Test against TSD 2 results ---
library(testthat)
library(dplyr)

tol <- 0.05
tol_dic <- 0.1

# TSD treatment codes
# trt_codes <- c(1 = "Diuretic",
#                2 = "Placebo",
#                3 = "Beta Blocker",
#                4 = "CCB",
#                5 = "ACE Inhibitor",
#                6 = "ARB")

# FE Relative effects
tsd_FE <- tribble(
~trt           , ~mean, ~sd , ~median, ~lower, ~upper,
"Placebo"      , -0.25, 0.06, -0.25  , -0.36 , -0.14 ,
"Beta Blocker" , -0.06, 0.06, -0.06  , -0.17 ,  0.05 ,
"CCB"          , -0.25, 0.05, -0.25  , -0.36 , -0.15 ,
"ACE Inhibitor", -0.36, 0.05, -0.36  , -0.46 , -0.25 ,
"ARB"          , -0.45, 0.06, -0.45  , -0.58 , -0.33 ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_FE_releff <- as.data.frame(relative_effects(db_fit_FE))

test_that("FE relative effects", {
  expect_equal(db_FE_releff$mean, tsd_FE$mean, tolerance = tol)
  expect_equal(db_FE_releff$sd, tsd_FE$sd, tolerance = tol)
  expect_equal(db_FE_releff$`50%`, tsd_FE$median, tolerance = tol)
  expect_equal(db_FE_releff$`2.5%`, tsd_FE$lower, tolerance = tol)
  expect_equal(db_FE_releff$`97.5%`, tsd_FE$upper, tolerance = tol)
})

# RE Relative effects
tsd_RE <- tribble(
~trt           , ~mean, ~sd , ~median, ~lower, ~upper,
"Placebo"      , -0.29, 0.09, -0.29  , -0.47 , -0.12 ,
"Beta Blocker" , -0.07, 0.09, -0.07  , -0.25 ,  0.10 ,
"CCB"          , -0.24, 0.08, -0.24  , -0.41 , -0.08 ,
"ACE Inhibitor", -0.40, 0.09, -0.40  , -0.58 , -0.24 ,
"ARB"          , -0.47, 0.11, -0.47  , -0.70 , -0.27 ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_RE_releff <- as.data.frame(relative_effects(db_fit_RE))

test_that("RE relative effects", {
  expect_equal(db_RE_releff$mean, tsd_RE$mean, tolerance = tol)
  expect_equal(db_RE_releff$sd, tsd_RE$sd, tolerance = tol)
  expect_equal(db_RE_releff$`50%`, tsd_RE$median, tolerance = tol)
  expect_equal(db_RE_releff$`2.5%`, tsd_RE$lower, tolerance = tol)
  expect_equal(db_RE_releff$`97.5%`, tsd_RE$upper, tolerance = tol)
})

# Heterogeneity SD
db_tau <- as.data.frame(summary(db_fit_RE, pars = "tau"))

test_that("RE heterogeneity SD", {
  expect_equal(db_tau$mean, 0.13, tolerance = tol)
  expect_equal(db_tau$sd, 0.04, tolerance = tol)
  expect_equal(db_tau$`50%`, 0.12, tolerance = tol)
  expect_equal(db_tau$`2.5%`, 0.05, tolerance = tol)
  expect_equal(db_tau$`97.5%`, 0.23, tolerance = tol)
})

# FE probabilities
tsd_pred_FE <- tribble(
~trt           , ~mean, ~sd  , ~median, ~lower, ~upper,
"Diuretic"     , 0.065, 0.067, 0.044  , 0.01  ,0.25   ,
"Placebo"      , 0.052, 0.055, 0.034  , 0.01  ,0.20   ,
"Beta Blocker" , 0.062, 0.064, 0.042  , 0.01  ,0.24   ,
"CCB"          , 0.051, 0.055, 0.034  , 0.01  ,0.20   ,
"ACE Inhibitor", 0.047, 0.050, 0.031  , 0.00  ,0.18   ,
"ARB"          , 0.043, 0.046, 0.028  , 0.00  ,0.17   ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_FE_pred <- as.data.frame(pred_FE)

test_that("FE predicted probabilities at 3 years", {
  expect_equal(db_FE_pred$mean, tsd_pred_FE$mean, tolerance = tol)
  expect_equal(db_FE_pred$sd, tsd_pred_FE$sd, tolerance = tol)
  expect_equal(db_FE_pred$`50%`, tsd_pred_FE$median, tolerance = tol)
  expect_equal(db_FE_pred$`2.5%`, tsd_pred_FE$lower, tolerance = tol)
  expect_equal(db_FE_pred$`97.5%`, tsd_pred_FE$upper, tolerance = tol)
})

# RE probabilities
tsd_pred_RE <- tribble(
~trt           , ~mean, ~sd  , ~median, ~lower, ~upper,
"Diuretic"     , 0.065, 0.067, 0.044  , 0.01  ,0.25   ,
"Placebo"      , 0.050, 0.053, 0.033  , 0.01  ,0.20   ,
"Beta Blocker" , 0.061, 0.064, 0.041  , 0.01  ,0.24   ,
"CCB"          , 0.052, 0.056, 0.035  , 0.01  ,0.20   ,
"ACE Inhibitor", 0.045, 0.048, 0.030  , 0.00  ,0.18   ,
"ARB"          , 0.042, 0.046, 0.028  , 0.00  ,0.17   ,
) %>% 
  mutate(trt = ordered(trt, levels = levels(db_net$treatments))) %>%
  arrange(trt)

db_RE_pred <- as.data.frame(pred_RE)

test_that("RE predicted probabilities at 3 years", {
  expect_equal(db_RE_pred$mean, tsd_pred_RE$mean, tolerance = tol)
  expect_equal(db_RE_pred$sd, tsd_pred_RE$sd, tolerance = tol)
  expect_equal(db_RE_pred$`50%`, tsd_pred_RE$median, tolerance = tol)
  expect_equal(db_RE_pred$`2.5%`, tsd_pred_RE$lower, tolerance = tol)
  expect_equal(db_RE_pred$`97.5%`, tsd_pred_RE$upper, tolerance = tol)
})

# RE DIC
test_that("RE DIC", {
  expect_equal(dic_RE$resdev, 53.7, tolerance = tol_dic)
  expect_equal(dic_RE$pd, 38.0, tolerance = tol_dic)
  expect_equal(dic_RE$dic, 91.7, tolerance = tol_dic)
})

# FE DIC
test_that("FE DIC", {
  expect_equal(dic_FE$resdev, 78.25, tolerance = tol_dic)
  expect_equal(dic_FE$pd, 27.0, tolerance = tol_dic)
  expect_equal(dic_FE$dic, 105.2, tolerance = tol_dic)
})
```
